### 2018-06-28 paper.tex
Initial commit

\documentclass[conference,compsoc]{IEEEtran}
% Some/most Computer Society conferences require the compsoc mode option,
% but others may want the standard conference format.
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[conference,compsoc]{../sty/IEEEtran}

\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{xcolor}
\newcommand\notes[1]{\textcolor{red}{#1}}

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/pkg/ifpdf
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

% *** CITATION PACKAGES ***
%
\ifCLASSOPTIONcompsoc
  % IEEE Computer Society needs nocompress option
  % requires cite.sty v4.0 or later (November 2003)
  \usepackage[nocompress]{cite}
\else
  % normal IEEE
  \usepackage{cite}
\fi
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of the IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off
% such as if a citation ever needs to be enclosed in parenthesis.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 5.0 (2009-03-20) and later if using hyperref.sty.
% The latest version can be obtained at:
% http://www.ctan.org/pkg/cite
% The documentation is contained in the cite.sty file itself.
%
% Note that some packages require special options to format as the Computer
% Society requires. In particular, Computer Society  papers do not use
% compressed citation ranges as is done in typical IEEE papers
% (e.g., [1]-[4]). Instead, they list every citation separately in order
% (e.g., [1], [2], [3], [4]). To get the latter we need to load the cite
% package with the nocompress option which is supported by cite.sty v4.0
% and later.

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation
% can be obtained at: 
% http://www.ctan.org/pkg/graphicx
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found at:
% http://www.ctan.org/pkg/epslatex
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

% *** MATH PACKAGES ***
%
\usepackage{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics.
%
% Note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/amsmath

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/pkg/algorithms
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/pkg/algorithmicx

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/array

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

% *** SUBFIGURE PACKAGES ***
%\ifCLASSOPTIONcompsoc
%  \usepackage[caption=false,font=footnotesize,labelfont=sf,textfont=sf]{subfig}
%\else
%  \usepackage[caption=false,font=footnotesize]{subfig}
%\fi
% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
% for subfigure.sty, the latter of which is no longer maintained and is
% incompatible with some LaTeX packages including fixltx2e. However,
% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
% which will override IEEEtran.cls' handling of captions and this will result
% in non-IEEE style figure/table captions. To prevent this problem, be sure
% and invoke subfig.sty's "caption=false" package option (available since
% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
% handling of captions.
% Note that the Computer Society format requires a sans serif font rather
% than the serif font used in traditional IEEE formatting and thus the need
% to invoke different subfig.sty package options depending on whether
% compsoc mode has been enabled.
%
% The latest version and documentation of subfig.sty can be obtained at:
% http://www.ctan.org/pkg/subfig

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure.
% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
% corrections already built into the system in which case a warning will
% be issued if an attempt is made to load fixltx2e.sty as it is no longer
% needed.
% The latest version and documentation can be found at:
% http://www.ctan.org/pkg/fixltx2e

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/stfloats
% Do not use the stfloats baselinefloat ability as the IEEE does not allow
% \baselineskip to stretch. Authors submitting work to the IEEE should note
% that the IEEE rarely uses double column equations and that authors should try
% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
% such ways.
% Do not attempt to use stfloats with fixltx2e as they are incompatible.
% Instead, use Morten Hogholm'a dblfloatfix which combines the features
% of both fixltx2e and stfloats:
%
% \usepackage{dblfloatfix}
% The latest version can be found at:
% http://www.ctan.org/pkg/dblfloatfix

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/url
% Basically, \url{my_url_here}.

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Resolving Limits Faced by Classical Machine Learning Approaches:\\Areas of Application for 
Collaborative Interactive Learning Techniques}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Christoph Sonntag$^1$}
\IEEEauthorblockA{$^1$Intelligent Systems Group, University of Passau, Innstrasse 70, Passau, Germany\\
sonntagc@fim.uni-passau.de}
}

% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass

% for over three affiliations, or if they all won't fit within the width
% of the page (and note that there is less available width in this regard for
% compsoc conferences compared to traditional conferences), use this
% alternative format:
% 
%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
%Homer Simpson\IEEEauthorrefmark{2},
%James Kirk\IEEEauthorrefmark{3}, 
%Montgomery Scott\IEEEauthorrefmark{3} and
%Eldon Tyrell\IEEEauthorrefmark{4}}
%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
%Georgia Institute of Technology,
%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
%Email: homer@thesimpsons.com}
%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212, Fax: (888) 555--1212}
%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

% make the title area
\maketitle

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
The area of \textit{Machine Learning (ML)} has experienced a high 
level of research interest in the last few years with it's underlying 
theory reaching back far into the 18Th century. Due to minimal 
costs for computation and the massive availability of data in the 
Internet recent research interest has been mainly focused on 
\textit{automatic ML (aML)}. In this ML paradigm a model 
(e.g.\ classifier, \dots) is being trained with a pre-labeled training 
set in order to make predictions on unknown unlabeled data. Problems arise 
in domains where data is rarely available or where the labeling process is 
too expensive (computationally or economically). Furthermore, real-world data 
can be uncertain, incomplete or contain noisy data. In these cases 
full automation is not reliable enough or even infeasible for specific 
domains. However, robust and trustworthy results are mandatory in a lot of 
applications like health informatics or autonomous vehicles. 
Therefore, systems are needed that interactively integrate knowledge from 
various experts, which can be collaborating humans or machines, in order 
to continuously improve results over a systems whole lifetime: So called 
\textit{Collaborative Interactive Learning (CIL)} systems.
This paper contributes in presenting an overview of classical ML approaches 
in comparison with CIL and outlines possible areas of application. 
\end{abstract}

\section{Introduction}
As with most concepts, there is no canonical 
definition for the term \textit{Machine Learning} but at its most basic form it 
can be described as algorithms that learn from a given set of training examples 
$\{(x_i, y_i)\}$ of inputs $x_i$ and outputs $y_i$ in order to 
make predictions on unknown input data. According to Tom 
Mitchell, a Computer Scientist from Carnegie Mellon University, ML tries 
to answer how we can build algorithms that automatically improve through 
experience and what fundamental laws govern all these learning processes\cite{ML:mitchell}.
The area of ML in general is a fast-growing discipline at the intersection of statistics 
and computer science and has experienced massive research interest in the last decades.
With its various application possibilities it has also been an interesting branch for 
economists and entrepreneurs.
Since ML scenarios like \textit{supervised}, \textit{unsupervised} and 
\textit{semi-supervised} learning, which we will cover later, are heavily data-driven, 
the Internet with its massive amount of data has contributed to the further development 
of research in the area of fully automated learning algorithms. Today, we can see the 
results in a variety of applications\cite{FoundationsOfML:mohri}\cite{DisciplineOfML:mitchell}, 
not limited to the list below.
\begin{itemize}
    \item \textit{Text classification, Natural Language Processing (NLP)}. 
        Many current mail programs have built-in spam detection which originally used
        simple regular expressions in order to detect phrases commonly used in spam mails.
        With state-of-the-art ML techniques it is not only possible for a mail program to 
        query for a number of words but to the pattern how spam mails are constructed and 
        to adapt itself to new types of spam.
    \item \textit{Speech recognition}. 
        Most commercial applications for speech recognition use ML to train itself to 
        recognize a users speech input. \notes{Umformen. Beschreiben, wofür ML genutzt wird.}
    \item \textit{Image recognition, OCR}.
        Machine Learning methods have also been successfully applied in domains where it's 
        important to extract information from images such as detecting and classifiying 
        objects or recognize handwritten \notes{only handwritten?} characters. Image 
        recognition and OCR are therefore for example used in medical diagnosis to 
        detect cancer on radiographs, in autonomous vehicles to detect obstacles and to 
        stay on track or in post-offices to sort envelopes with hand-written addresses. 
        \notes{Nochmal eine Quellenangabe?}
    \item \textit{Games}.
        Computer Games ususally offer a Multiplayer mode where a user can interact and 
        play the game even without a human opponent. For games with a small number of 
        possible moves after each turn, and therefore a realtively small game tree conatining 
        all possible moves, the minimax algorithm\cite{Prog2:bachmaier} can be sufficient. 
        It figures out which next move would minimize the worst-case scenario for all subsequent 
        moves. Therefore, it needs to know all possible moves, which can easily be computationally 
        infeasible for games like Chess or AlphaGo where a general move faces between 35 (Chess) and 
        250 (AlphaGo) possible subsequent game states.
        In order to still have challenging opponents modern Games are using ML to gain experience 
        by themselves.
    \item \textit{Search engines, Recommendation systems}.
        Nearly all current search machines use ML in one fashion or another. They mainly use these 
        techniques for \textit{(1) User classification}\notes{[q?]} in order to offer personalized 
        search results and for \textit{(2) Query classification} in order to ``understand' a 
        users query and to provide further meaningful information.
\end{itemize}

Despite the successfull application of ML in a lot of fields, most of these examples 
need a sufficient amount of labeled training data ($x_i$ with assigned $y_i$) in order to make 
correct predictions on or discover structured patterns in unknown data $x_j$. However, most 
data sets in the biomedical domain, in robotics or in other fields, where data is collected 
from sensor systems or other unreliable sources, are often either not available (e.g.\ rare 
diseases, borderline cases in road traffic, \dots) or contain noisy data, dirty data or unwanted 
data due to dirty sensors or poor visibility conditions in camera applications.
In addition, a machine learning algorithms prediction is solely based on the training data it 
has seen before. One might argue, that human decisions are also only based on experience they have 
made since their childhood but humans are often still superior to most algorithms in terms of 
the instinctive interpretation of complex patterns. Furthermore, they can learn to recognize 
structural patterns from very few training data.

\begin{figure}[!h]
\centering
\includegraphics[width=3.5in]{images/CIL}
\caption{Collaborative Interactive Learning.}
\label{fig:CIL}
\end{figure}

Hence, \textit{Collaborative Interactive Learning (CIL)} includes domain experts (humans) 
and other CIL systems in the decision/prediction making process as shown in 
Figure~\ref{fig:CIL}. The relatively new term describes a new 
generation of systems with
\begin{itemize}
    \item lifelong learning capabilities in order to continuously improve its 
        knowledge base
    \item and the ability to exchange knowledge with other CIL systems as well as humans 
        in order to improve the own knowledge and the one of other entities in a 
        bi-directional way\cite{CIL:sick}.
\end{itemize}
This article gives a brief introduction on possible areas of application for the CIL-approach. 
It starts with an overview of classical machine learning scenarios, discussing where they are 
facing limits and motivating the use of CIL\@. It then lists possble applications and concludes 
with a view on future research interests.\notes{Relation to Organic Computing?}

\section{Algorithmic Foundations}
Bevor wir uns genauer den Anwendungen und Herausforderungen von CIL widmen, schauen wir uns 
zuerst vorhandene machine learning Strategien und Algorithmen an. Wie oben bereits angedeutet, 
gibt es eine Vielzahl an Definitionen für den Begriff ML\@. Hauptsächlich hat jedoch Arthur Samuel 
diesen Begriff im Jahr 1959 geprägt. Seitdem hat sich in diesem Bereich natürlich einiges geändert, 
jedoch gilt die Definition, dass ML Computern erlaubt Probleme zu lösen, ohne speziell dafür 
programmiert zu sein, heute immer noch\cite{MLStudiesUsingCheckers:samuel}.

Über die letzten Jahrzehnte hat sich ML stark weiterentwickelt und ist zu einem Bereich 
starken Forschungsinteresse vieler verschiedener Akteure geworden, was es schwierig macht, 
Lern-Strategien in verschiedene Kategorien einzuteilen. Unterschiedliche Forscher nutzen 
dazu verschiedene Ansätze\cite{FoundationsOfML:mohri}\cite{Structure:corne}. Im folgenden 
wollen wir fünf Strategien vorstellen\cite{FoundationsOfML:mohri}.

\subsection{Supervised learning}
Basically supervised learning is the way of learning from labeled examples and making predictions 
for all unseen points. This is the most basic concept of ML and used in a variety of applications 
where labeled data is easy to obtain. The spam mail example discussed in the introduction is an 
instance of supervised learning.

\subsection{Unsupervised learning}
Im Gegensatz zu supervised learning erhält der Lernende mit dieser Technik ausschließlich 
unlabeled training data und macht Vorraussagen für alle ungesehene Punkte. Diese Technik ist 
relativ ähnlich zu der Art, wie Säuglinge neue Sachen lernen (Lernen von Sprache) und 
findet zum Beispiel Einsatz im Clustering von Daten in Gruppen\cite{BrainInf:holzinger}.

\subsection{Semi-supervised learning}
Wie der Name suggeriert erhält der Lernende bei dieser Technik Trainingsdaten, die sowohl aus 
labeled als auch aus unlabeled data besteht und macht Vorraussagen für alle ungesehenen Punkte.
Diese Technik wird hauptsählich in Bereichen eingesetzt, in denen Daten leicht zu erreichen sind, 
aber das finden von passenden Labels teuer ist.

\subsection{Reinforcement Learning}\label{reinforcement}
Reinforcement Learning ist der wohl älteste Ansatz und ein potentiell wichtiger Ansatz für CIL\@. 
Der Lernende interagiert mit seiner Umgebung, um neue Informationen zu gewinnen. Für jede Aktion 
erhält er eine Belohnung. Sein Ziel ist es über mehrere Wiederholungen seine Belohnung zu 
maximieren. Er befindet sich so jedoch im Zwiespalt zwischen der Entscheidung bereits gewonnene 
Information auszunutzen oder mehr Informationen durch weiter Aktionen zu erhalten.

\subsection{Active Learning}\label{active}
Das Ziel von Active Learning ist es, durch geschicktes interaktives Agieren mit anderen Agenten 
bereits vorhandene Datenpunkte zu beschriften und so eine ähnliche Performance bei weniger 
Informationen zu erreichen, wie in der Methode des supervised learning. Um das zu erreichen, 
benötigt der Lernende eine Auswahlstrategie\cite{ActiveToDedicated:calma}, die entscheidet ob 
eine Aktion einen ausreichend großen für das beschriften eines Datenpunkts bringt oder nicht.

\section{When is using CIL helpful?}
In etablierten ML Systemen muss für jede spezielle Anwendung ein eigenes Modell im Voraus 
entworfen und trainiert werden. ML Systeme haben also einen relativ schmalen Anwendungsrahmen. 
Die Idee bei CIL-Systemen ist, dass sie ein Leben lang lernen und selbstorganisiert Wissen 
aus verschiedenen Quellen sammeln und auswerten, um so gemeinsam mit anderen technischen 
und menschlichen Agenten kollaborierend und austauschend Probleme lösen\cite{CIL:sick}. 
Der CIL-Ansatz integriert also ganz bewusst andere intelligente Systeme 
(Menschen und Maschinen) in den Entscheidungsprozess, um für die einzelnen Entitäten 
ansonsten schwierige Probleme einfacher zu lösen.
Ein weiterer Unterschied zu klassischen Ansätzen stellt der wechselseitig Nutzen dar. 
Maschinen profitieren nicht nur von Trainingsdaten anderer Agenten, sondern leisten 
einen eigenen Beitrag, um Kollaborationsprozesse von Menschen aktiv zu unterstützen, indem 
sie ihre Wünsche und Bedürfnisse erkennen und entsprechend reagieren\cite{CIL:sick}.

\section{Classification of CIL in Organic Computing}
CIL-Systeme können sozusagen teilweise als organisch strukturierte Informationstechnologie verstanden 
werden, die sogenannte Selbst-x-Eigenschaften erfüllen\cite{Organic:schloer}\cite{Organic:schmeck}, 
sich also 
\begin{itemize}
    \item selbst konfigurieren, in dem Sinn, dass sie nicht von Entwicklern auf einen 
        Anwendungsfall ausgerichtet werden, 
    \item selbst optimieren, indem sie verschiedene Strategien des ML anwenden, um ihr 
        Wissen zu erweitern, 
    \item und sich selbst heilen und schützen, da Kooperation mit anderen System möglich ist.
\end{itemize}
Je nachdem welche Methoden des ML eingesetzt werden sind CIL-Systeme mehr oder weniger 
selbst erklärend\cite{Organic:schloer}.

\section{Application examples}

\begin{itemize}
    \item Clustering
        \begin{itemize}
            \item (clustering communities on Facebook for group target advertising (politics))
            \item Methods: k-Means, DJ-clustering? --> add paper ref
        \end{itemize}
    \item Stock trading
    \item Health domain
        \begin{itemize}
            \item Detecting cancer on radon, Prof. Sauer/Forwiss research?
            \item Growing number of users are using smartphones sensors and related devices for 
                collating a range of health information, track regularly and detect patterns (noise?, privacy?)
        \end{itemize}
    \item Industry 4.0
        \begin{itemize}
            \item quality assurance
        \end{itemize}
    \item Agriculture
        \begin{itemize}
            \item Detecting bad grains, $\rightarrow$ Hackzurich project
        \end{itemize}
\end{itemize}

\section{Limitations/Challenges}
Challenges

\section{Conclusion/Future Directions}
The conclusion goes here.

% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation results for the network.}
%\label{fig_sim}
%\end{figure}

% Note that the IEEE typically puts floats only at the top, even when this
% results in a large percentage of a column being occupied by floats.

% An example of a double column floating figure using two subfigures.
% (The subfig.sty package must be loaded for this to work.)
% The subfigure \label commands are set within each subfloat command,
% and the \label for the overall figure must come after \caption.
% \hfil is used as a separator to get equal spacing.
% Watch out that the combined width of all the subfigures on a 
% line do not exceed the text width or a line break will occur.
%
%\begin{figure*}[!t]
%\centering
%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
%\label{fig_first_case}}
%\hfil
%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
%\label{fig_second_case}}
%\caption{Simulation results for the network.}
%\label{fig_sim}
%\end{figure*}
%
% Note that often IEEE papers with subfigures do not employ subfigure
% captions (using the optional argument to \subfloat[]), but instead will
% reference/describe all of them (a), (b), etc., within the main caption.
% Be aware that for subfig.sty to generate the (a), (b), etc., subfigure
% labels, the optional argument to \subfloat must be present. If a
% subcaption is not desired, just leave its contents blank,
% e.g., \subfloat[].

% An example of a floating table. Note that, for IEEE style tables, the
% \caption command should come BEFORE the table and, given that table
% captions serve much like titles, are usually capitalized except for words
% such as a, an, and, as, at, but, by, for, in, nor, of, on, or, the, to
% and up, which are usually not capitalized unless they are the first or
% last word of the caption. Table text will default to \footnotesize as
% the IEEE normally uses this smaller font for tables.
% The \label must come after \caption as always.
%
%\begin{table}[!t]
%% increase table row spacing, adjust to taste
%\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
%\caption{An Example of a Table}
%\label{table_example}
%\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
%\begin{tabular}{|c||c|}
%\hline
%One & Two\\
%\hline
%Three & Four\\
%\hline
%\end{tabular}
%\end{table}

% Note that the IEEE does not put floats in the very first column
% - or typically anywhere on the first page for that matter. Also,
% in-text middle ("here") positioning is typically not used, but it
% is allowed and encouraged for Computer Society conferences (but
% not Computer Society journals). Most IEEE journals/conferences use
% top floats exclusively. 
% Note that, LaTeX2e, unlike IEEE journals/conferences, places
% footnotes above bottom floats. This can be corrected via the
% \fnbelowfloat command of the stfloats package.

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)

\begin{thebibliography}{1}
\bibitem{ML:mitchell}
    Mitchell, T. M. (1997). Machine learning. 1997. Burr Ridge, IL: McGraw Hill, 45(37), 870-877.
\bibitem{FoundationsOfML:mohri}
    Mohri, M., Rostamizadeh, A., \& Talwalkar, A. (2012). Foundations of machine learning. MIT press.
\bibitem{DisciplineOfML:mitchell}
    Mitchell, T. M. (2006). The discipline of machine learning (Vol. 9). Carnegie Mellon University, School of Computer Science, Machine Learning Department.
\bibitem{Prog2:bachmaier}
    Bachmaier, C. (2017). Lecture. Programming II\@. Faculty for Informatics and Mathematics, University of Passau, Germany.\notes{check this}
\bibitem{CIL:sick}
    Sick, B., Oeste-Rei{\ss}, S., Schmidt, A., Tomforde, S., \& Zweig, A. K. (2018). Collaborative Interactive Learning. Informatik-Spektrum, 41(1), 52-55.
\bibitem{Structure:corne}
    Corne, D., Dhaenens, C., \& Jourdan, L. (2012). Synergies between operations research and data mining: The emerging use of multi-objective approaches. European Journal of Operational Research, 221(3), 469-479.
\bibitem{ActiveToDedicated:calma}
    Calma, A., Leimeister, J. M., Lukowicz, P., Oeste-Rei{\ss}, S., Reitmaier, T., Schmidt, A., \dots \& Zweig, K. A. (2016, April). From active learning to dedicated collaborative interactive learning. In ARCS 2016; 29th International Conference on Architecture of Computing Systems; Proceedings of (pp. 1-8). VDE.
\bibitem{BrainInf:holzinger}
    Holzinger, A. (2016). Interactive machine learning for health informatics: when do we need the human-in-the-loop?. Brain Informatics, 3(2), 119-131.
\bibitem{MLStudiesUsingCheckers:samuel}
    Samuel, A. L. (1959). Some studies in machine learning using the game of checkers. IBM Journal of research and development, 3(3), 210-229.
\bibitem{Organic:schloer}
    M{\"u}ller-Schloer, C., von der Malsburg, C., \& W{\"u}rt, R. P. (2004). Organic computing. Informatik-Spektrum, 27(4), 332-336.
\bibitem{Organic:schmeck}
    Schmeck, H. (2005, May). Organic computing-a new vision for distributed embedded systems. In Object-Oriented Real-Time Distributed Computing, 2005. ISORC 2005. Eighth IEEE International Symposium on (pp. 201-203). IEEE.
\end{thebibliography}

\end{document}

### 2018-06-29 paper.tex
Add classification in Organic Computing

@@
 
-\usepackage[ngerman]{babel}
-\usepackage{amsmath}
 \usepackage{xcolor}
@@
 in comparison with CIL and outlines possible areas of application. 
+\notes{Abstract kuerzen, 18th Jahrhundert interessiert niemanden.}
 \end{abstract}
@@
 \end{itemize}
+
 This article gives a brief introduction on possible areas of application for the CIL-approach. 
@@
 
-\section{When is using CIL helpful?}
+\section{When is using CIL helpful?}\label{AdvantageOfCIL}
 In etablierten ML Systemen muss für jede spezielle Anwendung ein eigenes Modell im Voraus 
@@
 sie ihre Wünsche und Bedürfnisse erkennen und entsprechend reagieren\cite{CIL:sick}.
+\notes{D-CIL und O-CIL, obwohl man unterscheidet, betrachten wir hier nur allgemeines Modell.}
 
@@
 \end{itemize}
-Je nachdem welche Methoden des ML eingesetzt werden sind CIL-Systeme mehr oder weniger 
-selbst erklärend\cite{Organic:schloer}.
+Je nachdem welche Methoden des ML eingesetzt werden, sind CIL-Systeme in der Entwicklung auch 
+mehr oder weniger selbst erklärend\cite{Organic:schloer}.
 
 \section{Application examples}
+\subsection{Clustering}
+
+\subsection{Health Domain}
+
+\subsection{Industry and Manufacturing}
+
+\subsection{Agriculture}
 
@@
         \end{itemize}
-    \item Stock trading
-    \item Health domain
+    \item Health
         \begin{itemize}
@@
         \end{itemize}
-    \item Industry 4.0
+    \item Industry and Manufacturing
         \begin{itemize}
@@
 IEEE.
+\bibitem{Foldit:web}
+    The Science Behind Foldit. (n.d.). Retrieved June 29, 2018, from https://fold.it/portal/info/about. University of Washington, Departments of Computer Science \& Engineering and Biochemistry.
 \end{thebibliography}

### 2018-06-29 paper.tex
Add clustering application section

@@
 \section{Algorithmic Foundations}
-Bevor wir uns genauer den Anwendungen und Herausforderungen von CIL widmen, schauen wir uns 
-zuerst vorhandene machine learning Strategien und Algorithmen an. Wie oben bereits angedeutet, 
-gibt es eine Vielzahl an Definitionen für den Begriff ML\@. Hauptsächlich hat jedoch Arthur Samuel 
-diesen Begriff im Jahr 1959 geprägt. Seitdem hat sich in diesem Bereich natürlich einiges geändert, 
-jedoch gilt die Definition, dass ML Computern erlaubt Probleme zu lösen, ohne speziell dafür 
-programmiert zu sein, heute immer noch\cite{MLStudiesUsingCheckers:samuel}.
+Before we take a closer look at the applications and challenges of CIL, first consider the 
+following existing machine learning strategies and algorithms. As already mentioned above, 
+there is a multitude of definitions for the term ML\@. But primarily, Arthur Samuel 
+coined this term in 1959. Of course, a lot has changed in this area since then, 
+however, the definition that ML allows computers to solve problems without being 
+specifically programmed to do so, is still valid today\cite{MLStudiesUsingCheckers:samuel}.
 
-Über die letzten Jahrzehnte hat sich ML stark weiterentwickelt und ist zu einem Bereich 
-starken Forschungsinteresse vieler verschiedener Akteure geworden, was es schwierig macht, 
-Lern-Strategien in verschiedene Kategorien einzuteilen. Unterschiedliche Forscher nutzen 
-dazu verschiedene Ansätze\cite{FoundationsOfML:mohri}\cite{Structure:corne}. Im folgenden 
-wollen wir fünf Strategien vorstellen\cite{FoundationsOfML:mohri}.
+Over the last decades, ML has developed significantly and has become an area of
+research interest for many different actors, which makes it difficult to divide learning 
+strategies into several categories. Different researchers are using different approaches 
+for that\cite{FoundationsOfML:mohri}\cite{Structure:corne}. 
+In the following section we want to present five strategies\cite{FoundationsOfML:mohri}.
 
@@
 \subsection{Unsupervised learning}
-Im Gegensatz zu supervised learning erhält der Lernende mit dieser Technik ausschließlich 
-unlabeled training data und macht Vorraussagen für alle ungesehene Punkte. Diese Technik ist 
-relativ ähnlich zu der Art, wie Säuglinge neue Sachen lernen (Lernen von Sprache) und 
-findet zum Beispiel Einsatz im Clustering von Daten in Gruppen\cite{BrainInf:holzinger}.
+In contrast to supervised learning, with this technique the learner only receives 
+unlabeled training data and makes predictions for all unseen points. This technique is 
+relatively similar to the way infants learn new things (e.g.\ learning a language) and 
+is used, for example, in clustering data into groups\cite{BrainInf:holzinger}.
 
 \subsection{Semi-supervised learning}
-Wie der Name suggeriert erhält der Lernende bei dieser Technik Trainingsdaten, die sowohl aus 
-labeled als auch aus unlabeled data besteht und macht Vorraussagen für alle ungesehenen Punkte.
-Diese Technik wird hauptsählich in Bereichen eingesetzt, in denen Daten leicht zu erreichen sind, 
-aber das finden von passenden Labels teuer ist.
+As the name suggests, the learner receives training data, which consists of both 
+labeled as well as unlabelled data and makes predictions for all unseen points.
+This technique is mainly used in areas where data is easily accessible, 
+but finding the right label is expensive.
 
 \subsection{Reinforcement Learning}\label{reinforcement}
-Reinforcement Learning ist der wohl älteste Ansatz und ein potentiell wichtiger Ansatz für CIL\@. 
-Der Lernende interagiert mit seiner Umgebung, um neue Informationen zu gewinnen. Für jede Aktion 
-erhält er eine Belohnung. Sein Ziel ist es über mehrere Wiederholungen seine Belohnung zu 
-maximieren. Er befindet sich so jedoch im Zwiespalt zwischen der Entscheidung bereits gewonnene 
-Information auszunutzen oder mehr Informationen durch weiter Aktionen zu erhalten.
+Reinforcement learning is probably the oldest approach and a potentially important one for CIL\@. 
+The learner interacts with his environment to gain new information. For each action 
+he'll gets a reward. His goal is to maximize his reward over several repetitions. 
+However, he is in conflict with using what has already been won by his actions 
+or to get more information through further actions.
 
 \subsection{Active Learning}\label{active}
-Das Ziel von Active Learning ist es, durch geschicktes interaktives Agieren mit anderen Agenten 
-bereits vorhandene Datenpunkte zu beschriften und so eine ähnliche Performance bei weniger 
-Informationen zu erreichen, wie in der Methode des supervised learning. Um das zu erreichen, 
-benötigt der Lernende eine Auswahlstrategie\cite{ActiveToDedicated:calma}, die entscheidet ob 
-eine Aktion einen ausreichend großen für das beschriften eines Datenpunkts bringt oder nicht.
+The goal of Active Learning is to interact with other agents in a clever way in order 
+to label already existing data points and thus achieve a similar performance at less available 
+Information as in the method of supervised learning. To achieve this, 
+the learner needs a selection strategy\cite{ActiveToDedicated:calma} that decides whether 
+an action has enough information content to label a data point or not.
 
 \section{When is using CIL helpful?}\label{AdvantageOfCIL}
-In etablierten ML Systemen muss für jede spezielle Anwendung ein eigenes Modell im Voraus 
-entworfen und trainiert werden. ML Systeme haben also einen relativ schmalen Anwendungsrahmen. 
-Die Idee bei CIL-Systemen ist, dass sie ein Leben lang lernen und selbstorganisiert Wissen 
-aus verschiedenen Quellen sammeln und auswerten, um so gemeinsam mit anderen technischen 
-und menschlichen Agenten kollaborierend und austauschend Probleme lösen\cite{CIL:sick}. 
-Der CIL-Ansatz integriert also ganz bewusst andere intelligente Systeme 
-(Menschen und Maschinen) in den Entscheidungsprozess, um für die einzelnen Entitäten 
-ansonsten schwierige Probleme einfacher zu lösen.
-Ein weiterer Unterschied zu klassischen Ansätzen stellt der wechselseitig Nutzen dar. 
-Maschinen profitieren nicht nur von Trainingsdaten anderer Agenten, sondern leisten 
-einen eigenen Beitrag, um Kollaborationsprozesse von Menschen aktiv zu unterstützen, indem 
-sie ihre Wünsche und Bedürfnisse erkennen und entsprechend reagieren\cite{CIL:sick}.
+In established ML systems, a separate model must be developed and trained in advance for 
+each specific application. ML systems therefore have a relatively narrow application frame. 
+The idea behind CIL systems is that they learn and self-organize knowledge throughout their lives. 
+They collect information from various sources and evaluate the obtained data, so that they 
+can solve problems together with other technical and human agents in a 
+collaborative and interchangeable way\cite{CIL:sick}.
+The CIL approach therefore deliberately integrates other intelligent systems 
+(people and machines) into the decision-making process in order to ensure that the individual entities 
+can solve otherwise difficult problems much easier.
+Another difference to classical approaches is the mutual benefit. 
+Machines not only benefit from training data of other agents, but also provide 
+an own contribution to actively support people's collaboration processes by 
+recognising their wishes and needs and reacting accordingly\cite{CIL:sick}.
 \notes{D-CIL und O-CIL, obwohl man unterscheidet, betrachten wir hier nur allgemeines Modell.}
@@
 \section{Classification of CIL in Organic Computing}
-CIL-Systeme können sozusagen teilweise als organisch strukturierte Informationstechnologie verstanden 
-werden, die sogenannte Selbst-x-Eigenschaften erfüllen\cite{Organic:schloer}\cite{Organic:schmeck}, 
-sich also 
+CIL systems can be understood as organically structured information technology
+which fulfill so-called self-x-properties\cite{Organic:schloer}\cite{Organic:schmeckt}.
+They
 \begin{itemize}
-    \item selbst konfigurieren, in dem Sinn, dass sie nicht von Entwicklern auf einen 
-        Anwendungsfall ausgerichtet werden, 
-    \item selbst optimieren, indem sie verschiedene Strategien des ML anwenden, um ihr 
-        Wissen zu erweitern, 
-    \item und sich selbst heilen und schützen, da Kooperation mit anderen System möglich ist.
+    \item configure themselves in the sense that they are not aligned by developers to an application case,
+    \item optimize themselves by applying various strategies of ML to expand their knowledge,
+    \item heal and protect themselves because cooperation with other systems is possible.
 \end{itemize}
-Je nachdem welche Methoden des ML eingesetzt werden, sind CIL-Systeme in der Entwicklung auch 
-mehr oder weniger selbst erklärend\cite{Organic:schloer}.
+Depending on which methods of ML are used, CIL systems are also more or less self-explanatory 
+during development\cite{Organic:schloer}.
 
@@
 \subsection{Clustering}
+Clustering is the perfect example of a starting point without sufficient information about a database. 
+The basic goal here is to divide a data set into homogeneous groups of individual data points in order to create structure.
+Clustering is used, for example, in most recommendation systems of popular Internet applications (Netflix movie recommendations, YouTube Video Tags \notes{[?]}) to group similar tags or find groups of people with a similar taste in movies.
+Furthermore, clustering is used to identify communities in social networks, for example for target-advertising, or to cluster location-data so that "important places" of a person can be identified.
+
+Unfortunately, real-world data in these areas is often unclean, contains false or unwanted data and is often present in 
+dimensions $>$3, so that people alone, who are otherwise very good at recognizing similarities, are dependent on ML and vice-versa.
+
+There are different approaches to cluster data into homogeneous groups.
+One of them is the k-Means algorithm\notes{[?]}.
+This requires at the beginning the number of $k$ clusters it should find.
+It then randomly places $k$ centroids in space, which should represent the center of a cluster, and assigns each item to the nearest centroid.
+After the assignment, each centroid is placed at the center of all items assigned to it.
+This process of assigning the items and moving the centroids to
+the center is now repeated until the assignments of the items no longer change.
+
+What all cluster algorithms have in common is that they need a way to compare data points for similarity.
+Classically, data points are tried to display in an n-dimensional metric space and, for example, their Euclidean distance is measured for similarity.
+The Euclidean distance between two data points $p = (p_1, p_2, \dots, p_n)$ and $q = (q_1, q_2, \dots, q_n)$ and thus their
+similarity, when a small result means more similar, is defined as
+\begin{equation}
+    similarity(p, q) = \sqrt{\sum_{i=1}^{n} (q_i - p_i)^{2}}.
+\end{equation}
+
+Since data is usually multidimensional, i.e.\ much larger than three, suitable attributes must be selected for the comparison. 
+However, the problem here is that similarity functions are influenced by subjective factors, since experts from different 
+fields also find different partial aspects of the amount of data to be investigated interesting.
+Therefore, the CIL approach can provide a decisive advantage in this case, as the knowledge and assessment of 
+different experts and other systems can be used to make such decisions.
+An interesting interactive approach follows\notes{[1]} to create a personal gazetteer from a users location data.
 
@@
 
-\begin{itemize}
-    \item Clustering
-        \begin{itemize}
-            \item (clustering communities on Facebook for group target advertising (politics))
-            \item Methods: k-Means, DJ-clustering? --> add paper ref
-        \end{itemize}
-    \item Health
-        \begin{itemize}
-            \item Detecting cancer on radon, Prof. Sauer/Forwiss research?
-            \item Growing number of users are using smartphones sensors and related devices for 
-                collating a range of health information, track regularly and detect patterns (noise?, privacy?)
-        \end{itemize}
-    \item Industry and Manufacturing
-        \begin{itemize}
-            \item quality assurance
-        \end{itemize}
-    \item Agriculture
-        \begin{itemize}
-            \item Detecting bad grains, $\rightarrow$ Hackzurich project
-        \end{itemize}
-\end{itemize}
-
-\section{Limitations/Challenges}
+\section{Challenges and future directions}
 Challenges
-
-\section{Conclusion/Future Directions}
-The conclusion goes here.
+Ethical Questions
 

### 2018-06-29 paper.tex
Finish conclusion

@@
 \subsection{Health Domain}
+Also and especially in medical diagnosis, doctors are often confronted with a very small amount of data.
+In rare diseases in particular, there are not enough training examples to use classical ML approaches efficiently and with a low error rate in practice.
+In many areas, such as emergency surgery, results are often required within a very short time, which makes pure ML techniques useless in many cases.
+After successfully completing their medical studies, however, doctors with relatively little experience already have the ability to examine and classify X-rays sufficiently accurately for various diseases and anomalies.
+In these cases the intuitiveness of one or more people can profitably support the CIL system.
+
+Another area of application in the field of medical research also takes advantage of human puzzle-solving intuition.
+The project "foldit" of the University of Washington has for years achieved remarkable results\notes{[?]} from the gamification of a problem related to biology.
+The researchers have developed a game that helps you to optimize and predict possible protein structures with the help of players\notes{[website]}.
+Proteins can fold in a number of different ways. Even with smaller proteins, the number of possible folds can be extremely high due to their many degrees of freedom.
+The aim of the game is to determine the optimal folding and thus the "most comfortable" state of a protein in order to be able to develop appropriate drugs for this shape.
+Since the structure determines the function of a protein\notes{[website]}, new forms can also be used to treat diseases such as AIDS or cancer more effectively.
+
+So we already see here a system that at least involves the human being as a collective form of knowledge acquisition in the solution of complex problems, even if not directly with technical systems.
+The next step towards CIL in this area could be to incorporate the results of human puzzle-solving into the calculations and decisions of ML systems in order to proactively support humans (bi-directional way of inputs) in finding solutions (for example by excluding unpromising folds).
 
 \subsection{Industry and Manufacturing}
+The primary goal in manufacturing is to keep production up and running under almost all circumstances. 
+Even short downtimes of production lines result in high sales losses for companies.
+This is why it is important to keep an eye on the wear of work equipment, production lines and the condition of machines in general at all times.
+Current systems already use various ML techniques\notes{[MLinManu]} to cover these applications.
 
-\subsection{Agriculture}
+For CIL systems, it is conceivable that, in addition to the sensor data used by the devices to "measure" wear, to call in expert knowledge so that rare cases that are easily recognisable as a suspicious situation for humans, can be identified at an early stage by the whole system.
+In this process, a CIL system must assess at runtime which expert should be asked what and when in order 
+to achieve maximum information content.
 
 \section{Challenges and future directions}
-Challenges
-Ethical Questions
+Since the field of Collaborative Interactive Learning is still a very new field of research, there is still a lot of 
+research to be done in the areas of continuous knowledge acquisition 
+and evaluation from several heterogeneous sources (Internet, expert knowledge, etc.), 
+and interaction with multiple other agents (humans and other CIL systems), 
+especially when systems have to adapt to changing situations during their lifetime.
+
+Not only technical difficulties have to be overcome, but also social ones. In order to use ML techniques effectively, 
+at least a minimum amount of data has to be provided in order to be analyzed. To do this, we need to decide 
+to what extent we are willing to disclose our data for the benefits of CIL systems and ML in general.
+Inhibitions in human-machine communication and interaction must also be overcome for CIL systems to be used successfully.
 

### 2018-08-11 paper.tex
Add recommendations from reviews

--- 2018-06-29 paper.tex
@@
-\documentclass[conference,compsoc]{IEEEtran}
+\documentclass[conference]{IEEEtran}
 % Some/most Computer Society conferences require the compsoc mode option,
@@
 % (uncomment the ones you want to load)
-
-% *** MISC UTILITY PACKAGES ***
-%
-%\usepackage{ifpdf}
-% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
-% compilation based on whether the output is pdf or dvi.
-% usage:
-% \ifpdf
-%   % pdf code
-% \else
-%   % dvi code
-% \fi
-% The latest version of ifpdf.sty can be obtained from:
-% http://www.ctan.org/pkg/ifpdf
-% Also, note that IEEEtran.cls V1.7 and later provides a builtin
-% \ifCLASSINFOpdf conditional that works the same way.
-% When switching from latex to pdflatex and vice-versa, the compiler may
-% have to be run twice to clear warning/error messages.
 
@@
 \fi
-% graphicx was written by David Carlisle and Sebastian Rahtz. It is
-% required if you want graphics, photos, etc. graphicx.sty is already
-% installed on most LaTeX systems. The latest version and documentation
-% can be obtained at: 
-% http://www.ctan.org/pkg/graphicx
-% Another good source of documentation is "Using Imported Graphics in
-% LaTeX2e" by Keith Reckdahl which can be found at:
-% http://www.ctan.org/pkg/epslatex
-%
-% latex, and pdflatex in dvi mode, support graphics in encapsulated
-% postscript (.eps) format. pdflatex in pdf mode supports graphics
-% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
-% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
-% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
-% which can result in "jaggedy"/blurry rendering of lines and letters as
-% well as large increases in file sizes.
-%
-% You can find documentation about the pdfTeX application at:
-% http://www.tug.org/applications/pdftex
 
@@
 
-%\usepackage{stfloats}
-% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
-% the ability to do double column floats at the bottom of the page as well
-% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
-% LaTeX2e). It also provides a command:
-%\fnbelowfloat
-% to enable the placement of footnotes below bottom floats (the standard
-% LaTeX2e kernel puts them above bottom floats). This is an invasive package
-% which rewrites many portions of the LaTeX2e float routines. It may not work
-% with other packages that modify the LaTeX2e float routines. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/pkg/stfloats
-% Do not use the stfloats baselinefloat ability as the IEEE does not allow
-% \baselineskip to stretch. Authors submitting work to the IEEE should note
-% that the IEEE rarely uses double column equations and that authors should try
-% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
-% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
-% such ways.
-% Do not attempt to use stfloats with fixltx2e as they are incompatible.
-% Instead, use Morten Hogholm'a dblfloatfix which combines the features
-% of both fixltx2e and stfloats:
-%
-% \usepackage{dblfloatfix}
-% The latest version can be found at:
-% http://www.ctan.org/pkg/dblfloatfix
-
 % *** PDF, URL AND HYPERLINK PACKAGES ***
@@
 \begin{document}
-%
-% paper title
-% Titles are generally capitalized except for words such as a, an, and, as,
-% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
-% not capitalized unless they are the first or last word of the title.
-% Linebreaks \\ can be used within to get better formatting as desired.
-% Do not put math or special symbols in the title.
-\title{Resolving Limits Faced by Classical Machine Learning Approaches:\\Areas of Application for 
+\title{Resolving Limits Faced by Classical Machine Learning Approaches: Areas of Application for 
 Collaborative Interactive Learning Techniques}
@@
 
-% conference papers do not typically use \thanks and this command
-% is locked out in conference mode. If really needed, such as for
-% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
-% after \documentclass
-
-% for over three affiliations, or if they all won't fit within the width
-% of the page (and note that there is less available width in this regard for
-% compsoc conferences compared to traditional conferences), use this
-% alternative format:
-% 
-%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
-%Homer Simpson\IEEEauthorrefmark{2},
-%James Kirk\IEEEauthorrefmark{3}, 
-%Montgomery Scott\IEEEauthorrefmark{3} and
-%Eldon Tyrell\IEEEauthorrefmark{4}}
-%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
-%Georgia Institute of Technology,
-%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
-%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
-%Email: homer@thesimpsons.com}
-%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
-%Telephone: (800) 555--1212, Fax: (888) 555--1212}
-%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}
-
-% use for special paper notices
-%\IEEEspecialpapernotice{(Invited Paper)}
-
 % make the title area
@@
 level of research interest in the last few years with it's underlying 
-theory reaching back far into the 18Th century. Due to minimal 
+theory reaching back far into the 18th century. Due to minimal 
 costs for computation and the massive availability of data in the 
@@
 various experts, which can be collaborating humans or machines, in order 
-to continuously improve results over a systems whole lifetime: So called 
+to continuously improve results over a system's whole lifetime: So called 
 \textit{Collaborative Interactive Learning (CIL)} systems.
@@
 in comparison with CIL and outlines possible areas of application. 
-\notes{Abstract kuerzen, 18th Jahrhundert interessiert niemanden.}
 \end{abstract}
 
-\section{Introduction}
+\section{Introduction}\label{sec:intro}
+\notes{[Introduce abbreviations again.]}
+\notes{[Introduction is too long, the examples shouldn't be in the introduction in detail.--> extra section]}
 As with most concepts, there is no canonical 
@@
 make predictions on unknown input data. According to Tom 
-Mitchell, a Computer Scientist from Carnegie Mellon University, ML tries 
+Mitchell, a computer scientist from Carnegie Mellon University,  ML tries 
 to answer how we can build algorithms that automatically improve through 
-experience and what fundamental laws govern all these learning processes\cite{ML:mitchell}.
+experience and which fundamental laws govern all these learning processes\cite{ML:mitchell}.
 The area of ML in general is a fast-growing discipline at the intersection of statistics 
@@
 \textit{semi-supervised} learning, which we will cover later, are heavily data-driven, 
-the Internet with its massive amount of data has contributed to the further development 
+the internet with its massive amount of data has contributed to the further development 
 of research in the area of fully automated learning algorithms. Today, we can see the 
@@
         With state-of-the-art ML techniques it is not only possible for a mail program to 
-        query for a number of words but to the pattern how spam mails are constructed and 
+        query for a number of words but to recognise patterns of how spam mails are constructed and 
         to adapt itself to new types of spam.
     \item \textit{Speech recognition}. 
-        Most commercial applications for speech recognition use ML to train itself to 
-        recognize a users speech input. \notes{Umformen. Beschreiben, wofür ML genutzt wird.}
+        Most commercial applications for speech recognition also use ML to train itself to 
+        recognise a user's speech input in order to perform further semantic analysis on
+        that data.
     \item \textit{Image recognition, OCR}.
         Machine Learning methods have also been successfully applied in domains where it's 
-        important to extract information from images such as detecting and classifiying 
-        objects or recognize handwritten \notes{only handwritten?} characters. Image 
+        important to extract information from images such as detecting and classifying 
+        objects or recognizing handwritten characters. Image 
         recognition and OCR are therefore for example used in medical diagnosis to 
         detect cancer on radiographs, in autonomous vehicles to detect obstacles and to 
-        stay on track or in post-offices to sort envelopes with hand-written addresses. 
-        \notes{Nochmal eine Quellenangabe?}
+        stay on track or in post-offices to sort envelopes with hand-written addresses
+        \cite{DisciplineOfML:mitchell}.
     \item \textit{Games}.
-        Computer Games ususally offer a Multiplayer mode where a user can interact and 
+        Computer Games usually offer a Multiplayer mode where a user can interact and 
         play the game even without a human opponent. For games with a small number of 
-        possible moves after each turn, and therefore a realtively small game tree conatining 
+        possible moves after each turn, and therefore a relatively small game tree containing 
         all possible moves, the minimax algorithm\cite{Prog2:bachmaier} can be sufficient. 
         It figures out which next move would minimize the worst-case scenario for all subsequent 
-        moves. Therefore, it needs to know all possible moves, which can easily be computationally 
+        moves. Therefore, it needs to know all possible moves, which can easily become computationally 
         infeasible for games like Chess or AlphaGo where a general move faces between 35 (Chess) and 
         250 (AlphaGo) possible subsequent game states.
-        In order to still have challenging opponents modern Games are using ML to gain experience 
+        In order to still have challenging opponents, modern Games are using ML to gain experience 
         by themselves.
@@
         Nearly all current search machines use ML in one fashion or another. They mainly use these 
-        techniques for \textit{(1) User classification}\notes{[q?]} in order to offer personalized 
+        techniques for \textit{(1) User classification}\cite{DisciplineOfML:mitchell} in order to offer personalized 
         search results and for \textit{(2) Query classification} in order to ``understand' a 
@@
 
-Despite the successfull application of ML in a lot of fields, most of these examples 
+Despite the successful application of ML in a lot of fields, most of these examples 
 need a sufficient amount of labeled training data ($x_i$ with assigned $y_i$) in order to make 
-correct predictions on or discover structured patterns in unknown data $x_j$. However, most 
+correct predictions on, or discover structured patterns in unknown data $x_j$. However, most 
 data sets in the biomedical domain, in robotics or in other fields, where data is collected 
-from sensor systems or other unreliable sources, are often either not available (e.g.\ rare 
+from sensor systems or other unreliable sources, often are either not available (e.g.\ rare 
 diseases, borderline cases in road traffic, \dots) or contain noisy data, dirty data or unwanted 
 data due to dirty sensors or poor visibility conditions in camera applications.
-In addition, a machine learning algorithms prediction is solely based on the training data it 
-has seen before. One might argue, that human decisions are also only based on experience they have 
+In addition, a machine learning algorithm's prediction is solely based on the training data it 
+has seen before. One might argue that human decisions are also only based on experience having been
 made since their childhood but humans are often still superior to most algorithms in terms of 
@@
 It starts with an overview of classical machine learning scenarios, discussing where they are 
-facing limits and motivating the use of CIL\@. It then lists possble applications and concludes 
-with a view on future research interests.\notes{Relation to Organic Computing?}
+facing limits, describing the relation to Organic Computing and motivating the use of CIL\@. 
+It then lists possible applications and concludes 
+with a view on future research interests.
 
 \section{Algorithmic Foundations}
-Before we take a closer look at the applications and challenges of CIL, first consider the 
+Before we take a closer look at the applications and challenges of CIL, let's first consider the 
 following existing machine learning strategies and algorithms. As already mentioned above, 
@@
 for that\cite{FoundationsOfML:mohri}\cite{Structure:corne}. 
-In the following section we want to present five strategies\cite{FoundationsOfML:mohri}.
+In the following section I want to present five strategies\cite{FoundationsOfML:mohri}.
+\notes{[Add examples for each classification.]}
 
@@
 for all unseen points. This is the most basic concept of ML and used in a variety of applications 
-where labeled data is easy to obtain. The spam mail example discussed in the introduction is an 
-instance of supervised learning.
+where labeled data is easy to obtain. The spam mail example discussed in the introduction is a 
+case of supervised learning.
 
 \subsection{Unsupervised learning}
-In contrast to supervised learning, with this technique the learner only receives 
+In contrast to supervised learning, the learner here receives only 
 unlabeled training data and makes predictions for all unseen points. This technique is 
 relatively similar to the way infants learn new things (e.g.\ learning a language) and 
-is used, for example, in clustering data into groups\cite{BrainInf:holzinger}.
+is used, for example, in clustering data into groups, which we will discuss later\cite{BrainInf:holzinger}.
+\notes{[Maybe Clustering as an example.]}
 
@@
 but finding the right label is expensive.
+\notes{[Example needed.]}
 
 \subsection{Reinforcement Learning}\label{reinforcement}
-Reinforcement learning is probably the oldest approach and a potentially important one for CIL\@. 
-The learner interacts with his environment to gain new information. For each action 
-he'll gets a reward. His goal is to maximize his reward over several repetitions. 
-However, he is in conflict with using what has already been won by his actions 
-or to get more information through further actions.
+Reinforcement learning is probably the oldest approach and a potentially important one for CIL\@.\notes{[why?]} 
+The learner constantly interacts with its environment to gain new information. For each action 
+he gets a reward. The goal of the learner is to maximize its reward over several repetitions. 
+However, he is in conflict with using the information which has already been discovered by his actions 
+or with getting more information through further actions.
+\notes{[too short.]}
 
@@
 to label already existing data points and thus achieve a similar performance at less available 
-Information as in the method of supervised learning. To achieve this, 
+information as in the method of supervised learning. To achieve this, 
 the learner needs a selection strategy\cite{ActiveToDedicated:calma} that decides whether 
 an action has enough information content to label a data point or not.
+\notes{[too short.]}
 
-\section{When is using CIL helpful?}\label{AdvantageOfCIL}
+\section{When using CIL is helpful}\label{AdvantageOfCIL}
 In established ML systems, a separate model must be developed and trained in advance for 
 each specific application. ML systems therefore have a relatively narrow application frame. 
-The idea behind CIL systems is that they learn and self-organize knowledge throughout their lives. 
+The idea behind CIL systems is that they learn, self-organize and improve knowledge throughout their lives. 
 They collect information from various sources and evaluate the obtained data, so that they 
@@
 Machines not only benefit from training data of other agents, but also provide 
-an own contribution to actively support people's collaboration processes by 
+an own contribution to actively support human collaboration processes by 
 recognising their wishes and needs and reacting accordingly\cite{CIL:sick}.
-\notes{D-CIL und O-CIL, obwohl man unterscheidet, betrachten wir hier nur allgemeines Modell.}
 
 \section{Classification of CIL in Organic Computing}
+\notes{[The author could introduce the domain of Organic Computing a little more in detail, e.g.\ by describing the self-x properties.]}
 CIL systems can be understood as organically structured information technology
-which fulfill so-called self-x-properties\cite{Organic:schloer}\cite{Organic:schmeckt}.
+which fulfill so-called self-x-properties\cite{Organic:schloer}\cite{Organic:schmeck}.
 They
@@
     \item optimize themselves by applying various strategies of ML to expand their knowledge,
-    \item heal and protect themselves because cooperation with other systems is possible.
+    \item heal and protect themselves because cooperation with other systems is possible and desired.
 \end{itemize}
@@
 during development\cite{Organic:schloer}.
+\notes{[why?]}
 
 \section{Application examples}
+In the following we will discuss some interesting application examples.
+
 \subsection{Clustering}
-Clustering is the perfect example of a starting point without sufficient information about a database. 
-The basic goal here is to divide a data set into homogeneous groups of individual data points in order to create structure.
-Clustering is used, for example, in most recommendation systems of popular Internet applications (Netflix movie recommendations, YouTube Video Tags \notes{[?]}) to group similar tags or find groups of people with a similar taste in movies.
-Furthermore, clustering is used to identify communities in social networks, for example for target-advertising, or to cluster location-data so that "important places" of a person can be identified.
+\notes{[Clustering is not really a domain on it's own but can be used to solve problems in health domain, etc.\ pp.]}
+\notes{[Clarify the k-Means Algorithm by pointing out the steps.]}
+Clustering is the perfect example of a starting point without sufficient information about an amount of data. 
+The basic goal here is to divide a data set into homogeneous groups of individual data points in order to create structure in it.
+In this context data points must be checked for similarity in some way.
+Clustering is used, for example, in most recommendation systems of popular internet applications (Netflix movie recommendations, YouTube Video Tags\cite{YouTube:pasca}) to group similar tags or find groups of people with a similar taste in movies.
+Furthermore, clustering is used to identify communities in social networks, for example for target-advertising, or to cluster location-data so that "important places" of a person can be identified\cite{DJ:frankowski}.
 
 Unfortunately, real-world data in these areas is often unclean, contains false or unwanted data and is often present in 
-dimensions $>$3, so that people alone, who are otherwise very good at recognizing similarities, are dependent on ML and vice-versa.
+dimensions $>$3, so that people alone, who are otherwise very good at recognizing similarities in dimensions $\le3$, are dependent on ML and vice-versa.
 
 There are different approaches to cluster data into homogeneous groups.
-One of them is the k-Means algorithm\notes{[?]}.
-This requires at the beginning the number of $k$ clusters it should find.
+One of them is the k-Means algorithm\cite{FoundationsOfML:mohri}.
+In the beginning it requires the number of $k$ clusters it is supposed to find.
 It then randomly places $k$ centroids in space, which should represent the center of a cluster, and assigns each item to the nearest centroid.
@@
 
-What all cluster algorithms have in common is that they need a way to compare data points for similarity.
-Classically, data points are tried to display in an n-dimensional metric space and, for example, their Euclidean distance is measured for similarity.
+What all cluster algorithms have in common is that they need a way to compare data points for similarity respectively distance.
+Classically, data points are tried to be displayed in an n-dimensional metric space and, for example, their Euclidean distance is measured for similarity.
 The Euclidean distance between two data points $p = (p_1, p_2, \dots, p_n)$ and $q = (q_1, q_2, \dots, q_n)$ and thus their
 similarity, when a small result means more similar, is defined as
-\begin{equation}
+\begin{equation*}
     similarity(p, q) = \sqrt{\sum_{i=1}^{n} (q_i - p_i)^{2}}.
-\end{equation}
+\end{equation*}
 
@@
 However, the problem here is that similarity functions are influenced by subjective factors, since experts from different 
-fields also find different partial aspects of the amount of data to be investigated interesting.
+fields also find different partial aspects of the amount of data that is examined interesting.
 Therefore, the CIL approach can provide a decisive advantage in this case, as the knowledge and assessment of 
 different experts and other systems can be used to make such decisions.
-An interesting interactive approach follows\notes{[1]} to create a personal gazetteer from a users location data.
+An interesting interactive approach follows\cite{DJ:frankowski}, which creates a personal gazetteer from a user's location data 
+by interactively asking the right questions after cleaning the data from unwanted noise.
 
 \subsection{Health Domain}
+Also and especially in medical diagnosis, doctors are often confronted with a very small amount of data.
+For rare diseases in particular, there are not enough training examples to use classical ML approaches efficiently and with a low error rate in practice.
+In many areas, such as emergency surgery, results are often required within a very short time, which makes pure ML techniques useless in a lot of cases.
+After successfully completing their medical studies, however, doctors, even with relatively little experience, already have the ability to examine and classify X-rays sufficiently accurately for various diseases and anomalies.
+In these cases the intuitiveness of one or more people can profitably support the CIL system.
+
+Another area of application in the field of medical research also takes advantage of human puzzle-solving intuition. 
+For years the project "foldit" of the University of Washington has achieved remarkable results\cite{Foldit:results} from the gamification of a problem related to biology.
+The researchers have developed a game that helps them to optimize and predict possible protein structures with the help of 
+players\cite{Foldit:web}.
+Proteins can fold in a number of different ways. Even with smaller proteins, the number of possible folds can be extremely high due to their many degrees of freedom.
+The aim of the game is to determine the optimal folding and thus the "most comfortable" state of a protein in order to be able to develop appropriate drugs for and with this shape.
+Since the structure determines the function of a protein\cite{Foldit:web}, new forms can also be used to treat diseases such as AIDS or cancer more effectively.
+
+So we already see a system in this field that at least involves the human being as a collective form of knowledge acquisition in the solution of complex problems, even if not directly with technical systems.
+The next step towards CIL in this area could be to incorporate the results of human puzzle-solving into the calculations and decisions of ML systems in order to proactively support humans (bi-directional way of inputs, see section~\ref{sec:intro}) in finding solutions (for example by excluding unpromising folds).
 
 \subsection{Industry and Manufacturing}
+The primary goal in manufacturing is to keep production up and running under almost all circumstances. 
+Even short downtimes of production lines result in high sales losses for companies.
+This is why it is important to keep an eye on the wear of work equipment, production lines and the condition of machines in general at all times.
+Current systems already use various ML techniques\cite{Manu:wuest} to cover these applications.
 
-\subsection{Agriculture}
+For CIL-systems, it is conceivable, in addition to the sensor data used by the devices to "measure" wear, to call in expert knowledge, so that rare cases that are easily recognisable as a suspicious situation for humans, can be identified at an early stage by the whole system.
+In this process, a CIL system must estimate at runtime which expert should be asked what and when in order 
+to achieve maximum information content.
 
 \section{Challenges and future directions}
-Challenges
-Ethical Questions
+Since the area of Collaborative Interactive Learning is a very new field of research, there is still a lot of 
+research to be done in the areas of continuous knowledge acquisition 
+and evaluation from several heterogeneous sources (Internet, expert knowledge, etc.), 
+as well as the interaction with multiple other agents (humans and other CIL systems), 
+especially when systems have to adapt to changing situations during their lifetime.
 
-% An example of a floating figure using the graphicx package.
-% Note that \label must occur AFTER (or within) \caption.
-% For figures, \caption should occur after the \includegraphics.
-% Note that IEEEtran v1.7 and later has special internal code that
-% is designed to preserve the operation of \label within \caption
-% even when the captionsoff option is in effect. However, because
-% of issues like this, it may be the safest practice to put all your
-% \label just after \caption rather than within \caption{}.
-%
-% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
-% option should be used if it is desired that the figures are to be
-% displayed while in draft mode.
-%
-%\begin{figure}[!t]
-%\centering
-%\includegraphics[width=2.5in]{myfigure}
-% where an .eps filename suffix will be assumed under latex, 
-% and a .pdf suffix will be assumed for pdflatex; or what has been declared
-% via \DeclareGraphicsExtensions.
-%\caption{Simulation results for the network.}
-%\label{fig_sim}
-%\end{figure}
-
-% Note that the IEEE typically puts floats only at the top, even when this
-% results in a large percentage of a column being occupied by floats.
-
-% An example of a double column floating figure using two subfigures.
-% (The subfig.sty package must be loaded for this to work.)
-% The subfigure \label commands are set within each subfloat command,
-% and the \label for the overall figure must come after \caption.
-% \hfil is used as a separator to get equal spacing.
-% Watch out that the combined width of all the subfigures on a 
-% line do not exceed the text width or a line break will occur.
-%
-%\begin{figure*}[!t]
-%\centering
-%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
-%\label{fig_first_case}}
-%\hfil
-%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
-%\label{fig_second_case}}
-%\caption{Simulation results for the network.}
-%\label{fig_sim}
-%\end{figure*}
-%
-% Note that often IEEE papers with subfigures do not employ subfigure
-% captions (using the optional argument to \subfloat[]), but instead will
-% reference/describe all of them (a), (b), etc., within the main caption.
-% Be aware that for subfig.sty to generate the (a), (b), etc., subfigure
-% labels, the optional argument to \subfloat must be present. If a
-% subcaption is not desired, just leave its contents blank,
-% e.g., \subfloat[].
-
-% An example of a floating table. Note that, for IEEE style tables, the
-% \caption command should come BEFORE the table and, given that table
-% captions serve much like titles, are usually capitalized except for words
-% such as a, an, and, as, at, but, by, for, in, nor, of, on, or, the, to
-% and up, which are usually not capitalized unless they are the first or
-% last word of the caption. Table text will default to \footnotesize as
-% the IEEE normally uses this smaller font for tables.
-% The \label must come after \caption as always.
-%
-%\begin{table}[!t]
-%% increase table row spacing, adjust to taste
-%\renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-%\caption{An Example of a Table}
-%\label{table_example}
-%\centering
-%% Some packages, such as MDW tools, offer better commands for making tables
-%% than the plain LaTeX2e tabular which is used here.
-%\begin{tabular}{|c||c|}
-%\hline
-%One & Two\\
-%\hline
-%Three & Four\\
-%\hline
-%\end{tabular}
-%\end{table}
-
-% Note that the IEEE does not put floats in the very first column
-% - or typically anywhere on the first page for that matter. Also,
-% in-text middle ("here") positioning is typically not used, but it
-% is allowed and encouraged for Computer Society conferences (but
-% not Computer Society journals). Most IEEE journals/conferences use
-% top floats exclusively. 
-% Note that, LaTeX2e, unlike IEEE journals/conferences, places
-% footnotes above bottom floats. This can be corrected via the
-% \fnbelowfloat command of the stfloats package.
-
-% trigger a \newpage just before the given reference
-% number - used to balance the columns on the last page
-% adjust value as needed - may need to be readjusted if
-% the document is modified later
-%\IEEEtriggeratref{8}
-% The "triggered" command can be changed if desired:
-%\IEEEtriggercmd{\enlargethispage{-5in}}
-
-% references section
-
-% can use a bibliography generated by BibTeX as a .bbl file
-% BibTeX documentation can be easily obtained at:
-% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
-% The IEEEtran BibTeX style support page is at:
-% http://www.michaelshell.org/tex/ieeetran/bibtex/
-%\bibliographystyle{IEEEtran}
-% argument is your BibTeX string definitions and bibliography database(s)
-%\bibliography{IEEEabrv,../bib/paper}
-%
-% <OR> manually copy in the resultant .bbl file
-% set second argument of \begin to the number of references
-% (used to reserve space for the reference number labels box)
+Not only technical difficulties have to be overcome, but also social ones. In order to use ML techniques effectively, 
+at least a minimum amount of data has to be provided in order to be analyzed. To do this, we need to decide 
+to what extent we are willing to disclose our data for the benefits of CIL systems and ML in general.
+Inhibitions in human-machine communication and interaction must also be overcome for CIL systems to be used 
+successfully and productively.
 
@@
 \bibitem{Prog2:bachmaier}
-    Bachmaier, C. (2017). Lecture. Programming II\@. Faculty for Informatics and Mathematics, University of Passau, Germany.\notes{check this}
+    Bachmaier, C. (2017). Lecture. Programming II\@. Faculty for Informatics and Mathematics, University of Passau, Germany.
 \bibitem{CIL:sick}
@@
 IEEE.
+\bibitem{DJ:frankowski}
+    Zhou, C., Frankowski, D., Ludford, P., Shekhar, S., \& Terveen, L.
+(2004, November).
+Discovering personal gazetteers: an interactive clustering approach.
+In Proceedings of the 12th annual ACM international workshop on Geographic information systems (pp.
+266-273).
+ACM.
+\bibitem{YouTube:pasca}
+    Toderici, G., Aradhye, H., Pasca, M., Sbaiz, L., \& Yagnik, J.
+(2010, June).
+Finding meaning on youtube: Tag recommendation and category discovery.
+In Computer Vision and Pattern Recognition (CVPR), 2010 IEEE Conference on (pp.
+3447-3454).
+IEEE.
 \bibitem{Foldit:web}
-    The Science Behind Foldit. (n.d.). Retrieved June 29, 2018, from https://fold.it/portal/info/about. University of Washington, Departments of Computer Science \& Engineering and Biochemistry.
+    The Science Behind Foldit.
+(n.d.).
+University of Washington, Departments of Computer Science \& Engineering and Biochemistry.
+Retrieved from \url{https://fold.it/portal/info/about} on June 29, 2018.
+\bibitem{Foldit:results}
+    Boyle, A., (2011, September). Gamers solve molecular puzzle that baffled scientists. Cosmic Log.\\
+    Retrieved from \url{https://cosmiclog.nbcnews.com/_news/2011/09/18/7802623-gamers-solve-molecular-puzzle-that-baffled-scientists} on June 29, 2018.
+\bibitem{Manu:wuest}
+    Wuest, T., Weimer, D., Irgens, C., \& Thoben, K. D. (2016). Machine learning in manufacturing: advantages, challenges, and applications. Production \& Manufacturing Research, 4(1), 23-45.
 \end{thebibliography}

### 2018-08-11 paper.tex
Reintroduce abbreviations in first section

@@
 \begin{abstract}
-The area of \textit{Machine Learning (ML)} has experienced a high 
+The area of \textit{Machine Learning} has experienced a high 
 level of research interest in the last few years with it's underlying 
@@
 Internet recent research interest has been mainly focused on 
-\textit{automatic ML (aML)}. In this ML paradigm a model 
+\textit{Automatic Machine Learning}. In this paradigm a model 
 (e.g.\ classifier, \dots) is being trained with a pre-labeled training 
@@
 \textit{Collaborative Interactive Learning (CIL)} systems.
-This paper contributes in presenting an overview of classical ML approaches 
-in comparison with CIL and outlines possible areas of application. 
+This paper contributes in presenting an overview of classical Machine Learning 
+approaches in comparison with CIL and outlines possible areas of application. 
 \end{abstract}
@@
 \section{Introduction}\label{sec:intro}
-\notes{[Introduce abbreviations again.]}
 \notes{[Introduction is too long, the examples shouldn't be in the introduction in detail.--> extra section]}
 As with most concepts, there is no canonical 
-definition for the term \textit{Machine Learning} but at its most basic form it 
+definition for the term \textit{Machine Learning (ML)} but at its most basic form it 
 can be described as algorithms that learn from a given set of training examples 
@@
         that data.
-    \item \textit{Image recognition, OCR}.
+    \item \textit{Image recognition, Optical Character Recognition (OCR)}.
         Machine Learning methods have also been successfully applied in domains where it's 

### 2018-08-11 paper.tex
Restructure the sections

@@
 \section{Introduction}\label{sec:intro}
-\notes{[Introduction is too long, the examples shouldn't be in the introduction in detail.--> extra section]}
 As with most concepts, there is no canonical 
@@
 of research in the area of fully automated learning algorithms. Today, we can see the 
-results in a variety of applications\cite{FoundationsOfML:mohri}\cite{DisciplineOfML:mitchell}, 
-not limited to the list below.
-\begin{itemize}
-    \item \textit{Text classification, Natural Language Processing (NLP)}. 
-        Many current mail programs have built-in spam detection which originally used
-        simple regular expressions in order to detect phrases commonly used in spam mails.
-        With state-of-the-art ML techniques it is not only possible for a mail program to 
-        query for a number of words but to recognise patterns of how spam mails are constructed and 
-        to adapt itself to new types of spam.
-    \item \textit{Speech recognition}. 
-        Most commercial applications for speech recognition also use ML to train itself to 
-        recognise a user's speech input in order to perform further semantic analysis on
-        that data.
-    \item \textit{Image recognition, Optical Character Recognition (OCR)}.
-        Machine Learning methods have also been successfully applied in domains where it's 
-        important to extract information from images such as detecting and classifying 
-        objects or recognizing handwritten characters. Image 
-        recognition and OCR are therefore for example used in medical diagnosis to 
-        detect cancer on radiographs, in autonomous vehicles to detect obstacles and to 
-        stay on track or in post-offices to sort envelopes with hand-written addresses
-        \cite{DisciplineOfML:mitchell}.
-    \item \textit{Games}.
-        Computer Games usually offer a Multiplayer mode where a user can interact and 
-        play the game even without a human opponent. For games with a small number of 
-        possible moves after each turn, and therefore a relatively small game tree containing 
-        all possible moves, the minimax algorithm\cite{Prog2:bachmaier} can be sufficient. 
-        It figures out which next move would minimize the worst-case scenario for all subsequent 
-        moves. Therefore, it needs to know all possible moves, which can easily become computationally 
-        infeasible for games like Chess or AlphaGo where a general move faces between 35 (Chess) and 
-        250 (AlphaGo) possible subsequent game states.
-        In order to still have challenging opponents, modern Games are using ML to gain experience 
-        by themselves.
-    \item \textit{Search engines, Recommendation systems}.
-        Nearly all current search machines use ML in one fashion or another. They mainly use these 
-        techniques for \textit{(1) User classification}\cite{DisciplineOfML:mitchell} in order to offer personalized 
-        search results and for \textit{(2) Query classification} in order to ``understand' a 
-        users query and to provide further meaningful information.
-\end{itemize}
+results in a variety of applications\cite{FoundationsOfML:mohri}\cite{DisciplineOfML:mitchell} 
+described in more detail in Section~\ref{sec:algos}.
+
+% List with current ML applications
 
@@
 the instinctive interpretation of complex patterns. Furthermore, they can learn to recognize 
-structural patterns from very few training data.
+structural patterns from very few training data. Hence, a new approach is needed in order to 
+counteract the disadvantages of classical ML\@.
+This article gives a brief introduction on possible areas of application for 
+\textit{Collaborative Interactive Learning (CIL)}. It starts with an overview of classical 
+machine learning scenarios, discussing where they are facing limits, describing the relation 
+to Organic Computing and motivating the use of CIL\@. It then lists possible applications 
+and concludes with a view on future research interests.
 
-\begin{figure}[!h]
-\centering
-\includegraphics[width=3.5in]{images/CIL}
-\caption{Collaborative Interactive Learning.}
-\label{fig:CIL}
-\end{figure}
-
-Hence, \textit{Collaborative Interactive Learning (CIL)} includes domain experts (humans) 
+\section{Collaborative Interactive Learning}\label{sec:cil}
+\notes{[More detail.]}
+CIL includes domain experts (humans) 
 and other CIL systems in the decision/prediction making process as shown in 
@@
 \end{itemize}
-
-This article gives a brief introduction on possible areas of application for the CIL-approach. 
-It starts with an overview of classical machine learning scenarios, discussing where they are 
-facing limits, describing the relation to Organic Computing and motivating the use of CIL\@. 
-It then lists possible applications and concludes 
-with a view on future research interests.
+\begin{figure}[!h]
+\centering
+\includegraphics[width=3.5in]{images/CIL}
+\caption{Interaction between heterogeneous systems in CIL.}
+\label{fig:CIL}
+\end{figure}
 
 \section{Algorithmic Foundations}
+\label{sec:algos}
 Before we take a closer look at the applications and challenges of CIL, let's first consider the 
@@
 strategies into several categories. Different researchers are using different approaches 
-for that\cite{FoundationsOfML:mohri}\cite{Structure:corne}. 
-In the following section I want to present five strategies\cite{FoundationsOfML:mohri}.
+\cite{FoundationsOfML:mohri}\cite{Structure:corne}. 
+However, in the following section I want to present five common strategies\cite{FoundationsOfML:mohri}.
 \notes{[Add examples for each classification.]}
@@
 \notes{[too short.]}
+
+\begin{itemize}
+    \item \textit{Text classification, Natural Language Processing (NLP)}. 
+        Many current mail programs have built-in spam detection which originally used
+        simple regular expressions in order to detect phrases commonly used in spam mails.
+        With state-of-the-art ML techniques it is not only possible for a mail program to 
+        query for a number of words but to recognise patterns of how spam mails are constructed and 
+        to adapt itself to new types of spam.
+    \item \textit{Speech recognition}. 
+        Most commercial applications for speech recognition also use ML to train itself to 
+        recognise a user's speech input in order to perform further semantic analysis on
+        that data.
+    \item \textit{Image recognition, Optical Character Recognition (OCR)}.
+        Machine Learning methods have also been successfully applied in domains where it's 
+        important to extract information from images such as detecting and classifying 
+        objects or recognizing handwritten characters. Image 
+        recognition and OCR are therefore for example used in medical diagnosis to 
+        detect cancer on radiographs, in autonomous vehicles to detect obstacles and to 
+        stay on track or in post-offices to sort envelopes with hand-written addresses
+        \cite{DisciplineOfML:mitchell}.
+    \item \textit{Games}.
+        Computer Games usually offer a Multiplayer mode where a user can interact and 
+        play the game even without a human opponent. For games with a small number of 
+        possible moves after each turn, and therefore a relatively small game tree containing 
+        all possible moves, the minimax algorithm\cite{Prog2:bachmaier} can be sufficient. 
+        It figures out which next move would minimize the worst-case scenario for all subsequent 
+        moves. Therefore, it needs to know all possible moves, which can easily become computationally 
+        infeasible for games like Chess or AlphaGo where a general move faces between 35 (Chess) and 
+        250 (AlphaGo) possible subsequent game states.
+        In order to still have challenging opponents, modern Games are using ML to gain experience 
+        by themselves.
+    \item \textit{Search engines, Recommendation systems}.
+        Nearly all current search machines use ML in one fashion or another. They mainly use these 
+        techniques for \textit{(1) User classification}\cite{DisciplineOfML:mitchell} in order to offer personalized 
+        search results and for \textit{(2) Query classification} in order to ``understand' a 
+        users query and to provide further meaningful information.
+\end{itemize}
 

### 2018-08-21 paper.tex
Extend section 2: COLLABORATIVE INTERACTIVE LEARNING

@@
 \section{Collaborative Interactive Learning}\label{sec:cil}
-\notes{[More detail.]}
-CIL includes domain experts (humans) 
-and other CIL systems in the decision/prediction making process as shown in 
-Figure~\ref{fig:CIL}. The relatively new term describes a new 
+The term \textit{Collaborative Interactive Learning (CIL)} is a relatively new concept of systems which 
+includes other domain experts (humans) and CIL systems in the decision/prediction making process 
+as shown in Figure~\ref{fig:CIL}. It describes the vision of a new 
 generation of systems with
@@
     \item lifelong learning capabilities in order to continuously improve its 
-        knowledge base
+        knowledge base (\textit{learning})
     \item and the ability to exchange knowledge with other CIL systems as well as humans 
-        in order to improve the own knowledge and the one of other entities in a 
-        bi-directional way\cite{CIL:sick}.
+        in order to improve the own knowledge and learning process and the one of other entities in a 
+        bi-directional way (\textit{interactive}, \textit{collaborative})\cite{CIL:sick}.
 \end{itemize}
@@
 \includegraphics[width=3.5in]{images/CIL}
-\caption{Interaction between heterogeneous systems in CIL.}
+\caption{Interaction between heterogeneous systems in CIL.\notes{own work}}
 \label{fig:CIL}
 \end{figure}
+So the main difference to classical ML is the possibilty to adapt and optimize itself during run-time 
+towards new situations without having been specifically trained for these use-cases whereas classical ML 
+systems have had to be fed with a sufficient amount of relevant training data\cite{CIL:sick}\cite{Organic:schloer}.
+Furthermore, CIL systems interact with their environment in order to not rely on a single training data set. 
+They collect data from several other systems (including humans) to validate already existing information and to 
+gather additional data from other sources. In this way, CIL systems can be used in a lot of application areas where 
+environments are constantly changing or training data is rarely available.
 
@@
 However, in the following section I want to present five common strategies\cite{FoundationsOfML:mohri}.
-\notes{[Add examples for each classification.]}
 
@@
 case of supervised learning.
+Many current mail programs have built-in spam detection which originally used
+simple regular expressions in order to detect phrases commonly used in spam mails.
+With state-of-the-art ML techniques it is not only possible for a mail program to 
+query for a number of words but to recognise patterns of how spam mails are constructed and 
+to adapt itself to new types of spam.
 
 \subsection{Unsupervised learning}
-In contrast to supervised learning, the learner here receives only 
-unlabeled training data and makes predictions for all unseen points. This technique is 
+In contrast to supervised learning, the learner receives only 
+unlabeled training data and makes predictions for all unseen points in this concept. This technique is 
 relatively similar to the way infants learn new things (e.g.\ learning a language) and 
 is used, for example, in clustering data into groups, which we will discuss later\cite{BrainInf:holzinger}.
-\notes{[Maybe Clustering as an example.]}
+Furthermore, nearly all current search machines use unsupervised learning strategies in one fashion or another. 
+They mainly use these techniques for \textit{(1) User classification}\cite{DisciplineOfML:mitchell} in order to offer personalized 
+search results and for \textit{(2) Query classification} in order to ``understand' a 
+users query and to provide further meaningful information. 
+\notes{[not sure if unsupervised; clustering and dimensionality reduction however is.]}
 
@@
 but finding the right label is expensive.
+Most commercial applications for speech recognition are using this technique to train itself to 
+recognise a user's speech input in order to perform further semantic analysis on
+that data. \notes{[not sure if unsupervised]}
 \notes{[Example needed.]}
@@
 \begin{itemize}
-    \item \textit{Text classification, Natural Language Processing (NLP)}. 
-        Many current mail programs have built-in spam detection which originally used
-        simple regular expressions in order to detect phrases commonly used in spam mails.
-        With state-of-the-art ML techniques it is not only possible for a mail program to 
-        query for a number of words but to recognise patterns of how spam mails are constructed and 
-        to adapt itself to new types of spam.
-    \item \textit{Speech recognition}. 
-        Most commercial applications for speech recognition also use ML to train itself to 
-        recognise a user's speech input in order to perform further semantic analysis on
-        that data.
     \item \textit{Image recognition, Optical Character Recognition (OCR)}.
@@
         by themselves.
-    \item \textit{Search engines, Recommendation systems}.
-        Nearly all current search machines use ML in one fashion or another. They mainly use these 
-        techniques for \textit{(1) User classification}\cite{DisciplineOfML:mitchell} in order to offer personalized 
-        search results and for \textit{(2) Query classification} in order to ``understand' a 
-        users query and to provide further meaningful information.
 \end{itemize}
@@
 \notes{[why?]}
+
+\subsection{Self-Configuration}
+\subsection{Self-Optimization}
+\subsection{Self- Healing and Protecting}
+\subsection{Self-Explanatory}
 
@@
 So we already see a system in this field that at least involves the human being as a collective form of knowledge acquisition in the solution of complex problems, even if not directly with technical systems.
-The next step towards CIL in this area could be to incorporate the results of human puzzle-solving into the calculations and decisions of ML systems in order to proactively support humans (bi-directional way of inputs, see section~\ref{sec:intro}) in finding solutions (for example by excluding unpromising folds).
+The next step towards CIL in this area could be to incorporate the results of human puzzle-solving into the calculations and decisions of ML systems in order to proactively support humans (bi-directional way of inputs, see Section~\ref{sec:intro}) in finding solutions
+for example by excluding unpromisingfls.
 

### 2018-08-23 paper.tex
Minor fixes

@@
 \textit{Collaborative Interactive Learning (CIL)} systems.
-This paper contributes in presenting an overview of classical Machine Learning 
+This paper contributes in presenting an overview of classical \textit{Machine Learning} 
 approaches in comparison with CIL and outlines possible areas of application. 
@@
 Basically supervised learning is the way of learning from labeled examples and making predictions 
-for all unseen points. This is the most basic concept of ML and used in a variety of applications 
-where labeled data is easy to obtain. The spam mail example discussed in the introduction is a 
-case of supervised learning.
+for all unseen points. This is the most basic concept of ML and is used in a variety of applications 
+where labeled data is easy to obtain. Spam mail detection for instance is a case where supervised learning 
+techniques are - among others - used.
 Many current mail programs have built-in spam detection which originally used
@@
 They mainly use these techniques for \textit{(1) User classification}\cite{DisciplineOfML:mitchell} in order to offer personalized 
-search results and for \textit{(2) Query classification} in order to ``understand' a 
+search results and for \textit{(2) Query classification} in order to ``understand'' a 
 users query and to provide further meaningful information. 
@@
 As the name suggests, the learner receives training data, which consists of both 
-labeled as well as unlabelled data and makes predictions for all unseen points.
+labeled as well as unlabeled data. Typically more unlabeled than labeled data.
 This technique is mainly used in areas where data is easily accessible, 
-but finding the right label is expensive.
+but finding the right label is hard.
 Most commercial applications for speech recognition are using this technique to train itself to 
 recognise a user's speech input in order to perform further semantic analysis on
-that data. \notes{[not sure if unsupervised]}
-\notes{[Example needed.]}
+that data. Obtaining a sufficient amount of labeled data, for example the transcriptions of 
+recorded audio files, would be expensive. Thus, unlabeled together with labeled data is being used 
+to train a learner in a meaningful way.
 
 \subsection{Reinforcement Learning}\label{reinforcement}
-Reinforcement learning is probably the oldest approach and a potentially important one for CIL\@.\notes{[why?]} 
+Reinforcement learning is probably the oldest approach and a potentially important one for CIL because 
+it constantly tries to reinforce its learning process and improve its behavior.\notes{[behavior vs behaviour]} 
 The learner constantly interacts with its environment to gain new information. For each action 
@@
 The goal of Active Learning is to interact with other agents in a clever way in order 
-to label already existing data points and thus achieve a similar performance at less available 
+to label already existing data points and thus achieve a similar performance with less available 
 information as in the method of supervised learning. To achieve this, 
@@
 \notes{[The author could introduce the domain of Organic Computing a little more in detail, e.g.\ by describing the self-x properties.]}
-CIL systems can be understood as organically structured information technology
-which fulfill so-called self-x-properties\cite{Organic:schloer}\cite{Organic:schmeck}.
-They
-\begin{itemize}
-    \item configure themselves in the sense that they are not aligned by developers to an application case,
-    \item optimize themselves by applying various strategies of ML to expand their knowledge,
-    \item heal and protect themselves because cooperation with other systems is possible and desired.
-\end{itemize}
+CIL systems can be described in many ways as \textit{organic}. In general, systems are being called organic, 
+if they fulfill so-called self-x-properties\cite{Organic:schloer}\cite{Organic:schmeck}.
+
+\subsection{Self-Configuration}
+They configure themselves in the sense that they are not aligned by developers to an application case.
+
+\subsection{Self-Optimization}
+They optimize themselves by applying various strategies of ML to expand their knowledge.
+
+\subsection{Self- Healing and Protecting}
+They heal and protect themselves because cooperation with other systems is possible and desired.
+
+\subsection{Self-Explanation}
 Depending on which methods of ML are used, CIL systems are also more or less self-explanatory 
@@
 \notes{[why?]}
-
-\subsection{Self-Configuration}
-\subsection{Self-Optimization}
-\subsection{Self- Healing and Protecting}
-\subsection{Self-Explanatory}
 
@@
 In this context data points must be checked for similarity in some way.
-Clustering is used, for example, in most recommendation systems of popular internet applications (Netflix movie recommendations, YouTube Video Tags\cite{YouTube:pasca}) to group similar tags or find groups of people with a similar taste in movies.
-Furthermore, clustering is used to identify communities in social networks, for example for target-advertising, or to cluster location-data so that "important places" of a person can be identified\cite{DJ:frankowski}.
+Clustering is used, for example, in most recommendation systems of popular internet applications 
+(\textit{Netflix} movie recommendations, \textit{YouTube} Video Tags\cite{YouTube:pasca}) to group similar tags or find groups 
+of people with a similar taste in movies.
+Furthermore, clustering can be used to identify communities in social networks, for example for target-advertising, or to cluster location-data so that "important places" of a person can be identified\cite{DJ:frankowski}.
 

### 2018-08-24 paper.tex
Add sections for Organic Computing and self-x properties

@@
 \includegraphics[width=3.5in]{images/CIL}
-\caption{Interaction between heterogeneous systems in CIL.\notes{own work}}
+\caption{Interaction between heterogeneous systems in CIL.}
 \label{fig:CIL}
 \end{figure}
-So the main difference to classical ML is the possibilty to adapt and optimize itself during run-time 
-towards new situations without having been specifically trained for these use-cases whereas classical ML 
+So the main difference to classical ML is the possibilty to adapt and optimise itself during run-time 
+towards new situations without having been specifically trained for these use-cases, whereas classical ML 
 systems have had to be fed with a sufficient amount of relevant training data\cite{CIL:sick}\cite{Organic:schloer}.
 Furthermore, CIL systems interact with their environment in order to not rely on a single training data set. 
-They collect data from several other systems (including humans) to validate already existing information and to 
+They collect data from several other sources (including humans) to validate already existing information and to 
 gather additional data from other sources. In this way, CIL systems can be used in a lot of application areas where 
 environments are constantly changing or training data is rarely available.
+In general, we can still distinguish between \textit{dedicated} (concentrating mostly on one defined learning process, 
+other interacting agents are largely human experts) and \textit{opportunistic} CIL (changing environments, heterogeneous 
+sources of information)\cite{CIL:sick}, 
+but we want to concentrate on general areas of application in this paper.
 
@@
 to adapt itself to new types of spam.
+Supervised Learning methods have also been successfully applied in domains where it's 
+important to extract information from images such as detecting and classifying 
+objects or recognizing handwritten characters. Image 
+recognition and OCR are therefore for example used in medical diagnosis to 
+detect cancer on radiographs, in autonomous vehicles to detect obstacles and to 
+stay on track or in post-offices to sort envelopes with hand-written addresses
+\cite{DisciplineOfML:mitchell}.
 
@@
 Furthermore, nearly all current search machines use unsupervised learning strategies in one fashion or another. 
-They mainly use these techniques for \textit{(1) User classification}\cite{DisciplineOfML:mitchell} in order to offer personalized 
-search results and for \textit{(2) Query classification} in order to ``understand'' a 
+They mainly use these techniques for \textit{(1) Ranking}, \textit{(2) User classification}\cite{DisciplineOfML:mitchell} 
+in order to offer personalized search results and for \textit{(3) Query classification} in order to ``understand'' a 
 users query and to provide further meaningful information.
-\notes{[not sure if unsupervised; clustering and dimensionality reduction however is.]}
 
@@
 Reinforcement learning is probably the oldest approach and a potentially important one for CIL because 
-it constantly tries to reinforce its learning process and improve its behavior.\notes{[behavior vs behaviour]} 
-The learner constantly interacts with its environment to gain new information. For each action 
-he gets a reward. The goal of the learner is to maximize its reward over several repetitions. 
+it constantly tries to reinforce its learning process and improve its behavior. 
+The learner constantly interacts with its environment to gain new information. A second instance interpretes the 
+actions a learner carries out and rewards it depending on the actions outcome for the environment. The goal of 
+the learner now is to maximize its reward over several repetitions. 
 However, he is in conflict with using the information which has already been discovered by his actions 
-or with getting more information through further actions.
-\notes{[too short.]}
-
-\subsection{Active Learning}\label{active}
-The goal of Active Learning is to interact with other agents in a clever way in order 
-to label already existing data points and thus achieve a similar performance with less available 
-information as in the method of supervised learning. To achieve this, 
-the learner needs a selection strategy\cite{ActiveToDedicated:calma} that decides whether 
-an action has enough information content to label a data point or not.
-\notes{[too short.]}
-
-\begin{itemize}
-    \item \textit{Image recognition, Optical Character Recognition (OCR)}.
-        Machine Learning methods have also been successfully applied in domains where it's 
-        important to extract information from images such as detecting and classifying 
-        objects or recognizing handwritten characters. Image 
-        recognition and OCR are therefore for example used in medical diagnosis to 
-        detect cancer on radiographs, in autonomous vehicles to detect obstacles and to 
-        stay on track or in post-offices to sort envelopes with hand-written addresses
-        \cite{DisciplineOfML:mitchell}.
-    \item \textit{Games}.
-        Computer Games usually offer a Multiplayer mode where a user can interact and 
+or with getting more information through further actions. Reinforcement Learning has been successfully 
+applied to various problems. 
+Computer games usually offer a multiplayer mode where a user can interact and 
 play the game even without a human opponent. For games with a small number of 
@@
 250 (AlphaGo) possible subsequent game states. 
-        In order to still have challenging opponents, modern Games are using ML to gain experience 
-        by themselves.
-\end{itemize}
+Therefore, game artificial intelligences like AlphaGo are using Reinforcement Learning in order to gain 
+experience by themselves\cite{Alpha:silver}.
+
+%\subsection{Active Learning}\label{active}
+%The goal of Active Learning is to interact with other agents in a clever way in order 
+%to label already existing data points and thus achieve a similar performance with less available 
+%information as in the method of supervised learning. To achieve this, 
+%the learner needs a selection strategy\cite{ActiveToDedicated:calma} that decides whether 
+%an action has enough information content to label a data point or not.
+%\notes{[Example needed.]}
 
@@
 \section{Classification of CIL in Organic Computing}
-\notes{[The author could introduce the domain of Organic Computing a little more in detail, e.g.\ by describing the self-x properties.]}
-CIL systems can be described in many ways as \textit{organic}. In general, systems are being called organic, 
-if they fulfill so-called self-x-properties\cite{Organic:schloer}\cite{Organic:schmeck}.
+The term ``organic'' can be intuitively described as structures being live-like and making decisions on their own. 
+A more formal way of characterizing even technical systems as organic is checking the applicability of 
+so-called self-x-properties\cite{Organic:schloer}\cite{Organic:schmeck}.
 
 \subsection{Self-Configuration}
-They configure themselves in the sense that they are not aligned by developers to an application case.
+A system is being called self-configurable, if it can modify its parameters on its own.
+CIL systems configure themselves in the sense that they are not aligned by developers to any narrow application 
+case but adapt their behavior in the current environment to its desired purpose.
 
 \subsection{Self-Optimization}
-They optimize themselves by applying various strategies of ML to expand their knowledge.
+In order to deliver reasonable output, a systems needs to constantly improve itself over its lifetime. Thus, parts of 
+the system have to analyze decisions made during run-time.
+CIL systems optimize themselves by applying various strategies of ML to expand their knowledge.
 
-\subsection{Self- Healing and Protecting}
-They heal and protect themselves because cooperation with other systems is possible and desired.
+\subsection{Self- Healing and Protection}
+Furthermore, if systems work in changing environments and interact with other agents, they're always exposed to 
+the risk of failure. Therefore, organic systems need to detect failures (either triggered by an own action or by an intruder) 
+and fix the faulty part.
+CIL systems in particular need to implement these features due to their desired interaction with multiple 
+other heterogeneous systems.
 
 \subsection{Self-Explanation}
-Depending on which methods of ML are used, CIL systems are also more or less self-explanatory 
-during development\cite{Organic:schloer}.
-\notes{[why?]}
+Ultimately, CIL systems need to stay self-explanatory. Due to the fact that they interact with a lot of other systems, over 
+different communication channels and in changing environments, networks of a massive amount of intelligent systems will arise. 
+Comprehending and understanding these structures even after a long period of time will be a difficult but important research 
+area in the field of CIL systems\cite{Organic:schloer}.
 
 \section{Application examples}
-In the following we will discuss some interesting application examples.
+In the following section we will discuss some interesting application examples.
 
 \subsection{Clustering}
-\notes{[Clustering is not really a domain on it's own but can be used to solve problems in health domain, etc.\ pp.]}
-\notes{[Clarify the k-Means Algorithm by pointing out the steps.]}
 Clustering is the perfect example of a starting point without sufficient information about an amount of data. 
@@
 In the beginning it requires the number of $k$ clusters it is supposed to find.
-It then randomly places $k$ centroids in space, which should represent the center of a cluster, and assigns each item to the nearest centroid.
+It then proceeds as follows:
+\begin{enumerate}
+    \item Randomly place $k$ centroids in space (these represent the center of a single cluster).
+    \item Assign each item in space to its nearest centroid.
+    \item Move each centroid to the center of all items assigned to it.
+    \item Repeat (2) and (3) until the assignments of the items no longer change.
+\end{enumerate}
+%It then randomly places $k$ centroids in space, which should represent the center of a cluster, and assigns each item to the nearest centroid.
 After the assignment, each centroid is placed at the center of all items assigned to it.
 This process of assigning the items and moving the centroids to
-the center is now repeated until the assignments of the items no longer change.
+%the center is now repeated until the assignments of the items no longer change.
 
-What all cluster algorithms have in common is that they need a way to compare data points for similarity respectively distance.
+What all cluster algorithms have in common is that they need a way to compare data points for similarity respectively distance 
+in order to find centers.
 Classically, data points are tried to be displayed in an n-dimensional metric space and, for example, their Euclidean distance is measured for similarity.
@@
     Holzinger, A. (2016). Interactive machine learning for health informatics: when do we need the human-in-the-loop?. Brain Informatics, 3(2), 119-131.
+\bibitem{Alpha:silver}
+    Silver, D., Hassabis, D.
+(2016, January).
+AlphaGo: Mastering the ancient game of Go with Machine Learning.
+Google AI Blog.
+Retrieved from \url{https://ai.googleblog.com/2016/01/alphago-mastering-ancient-game-of-go.html} on August 24, 2018.
 \bibitem{MLStudiesUsingCheckers:samuel}
@@
 \bibitem{Foldit:results}
-    Boyle, A., (2011, September). Gamers solve molecular puzzle that baffled scientists. Cosmic Log.\\
+    Boyle, A. (2011, September). Gamers solve molecular puzzle that baffled scientists. Cosmic Log.\\
     Retrieved from \url{https://cosmiclog.nbcnews.com/_news/2011/09/18/7802623-gamers-solve-molecular-puzzle-that-baffled-scientists} on June 29, 2018.

### 2018-09-12 CILApplicationAreas.tex
Finish publishable version

--- 2018-08-24 paper.tex
@@
 \author{\IEEEauthorblockN{Christoph Sonntag$^1$}
-\IEEEauthorblockA{$^1$Intelligent Systems Group, University of Passau, Innstrasse 70, Passau, Germany\\
+\IEEEauthorblockA{$^1$Intelligent Systems Group, University of Passau, Innstrasse 43, Passau, Germany\\
 sonntagc@fim.uni-passau.de}
@@
 applications like health informatics or autonomous vehicles. 
-Therefore, systems are needed that interactively integrate knowledge from 
+Therefore, systems are required which interactively integrate knowledge from 
 various experts, which can be collaborating humans or machines, in order 
@@
 Since ML scenarios like \textit{supervised}, \textit{unsupervised} and 
-\textit{semi-supervised} learning, which we will cover later, are heavily data-driven, 
+\textit{semi-supervised} learning, which will be covered later, are heavily data-driven, 
 the internet with its massive amount of data has contributed to the further development 
-of research in the area of fully automated learning algorithms. Today, we can see the 
-results in a variety of applications\cite{FoundationsOfML:mohri}\cite{DisciplineOfML:mitchell} 
+of research in the area of fully automated learning algorithms. Today, the results can 
+be seen in a variety of applications\cite{FoundationsOfML:mohri}\cite{DisciplineOfML:mitchell} 
 described in more detail in Section~\ref{sec:algos}.
@@
 The term \textit{Collaborative Interactive Learning (CIL)} is a relatively new concept of systems which 
-includes other domain experts (humans) and CIL systems in the decision/prediction making process 
+include other domain experts (humans) and CIL systems in the decision/prediction making process 
 as shown in Figure~\ref{fig:CIL}. It describes the vision of a new 
@@
 \centering
-\includegraphics[width=3.5in]{images/CIL}
+\includegraphics[width=3.5in]{CIL}
 \caption{Interaction between heterogeneous systems in CIL.}
@@
 \end{figure}
-So the main difference to classical ML is the possibilty to adapt and optimise itself during run-time 
+So the main difference to classical ML is the possibility to adapt and optimise itself during run-time 
 towards new situations without having been specifically trained for these use-cases, whereas classical ML 
@@
 sources of information)\cite{CIL:sick}, 
-but we want to concentrate on general areas of application in this paper.
+but in order to give a general overview on areas of application, both will be considered equal in this paper.
 
@@
 research interest for many different actors, which makes it difficult to divide learning 
-strategies into several categories. Different researchers are using different approaches 
-\cite{FoundationsOfML:mohri}\cite{Structure:corne}. 
+strategies into several categories. Different researchers are using different 
+approaches\cite{FoundationsOfML:mohri}\cite{Structure:corne}. 
 However, in the following section I want to present five common strategies\cite{FoundationsOfML:mohri}.
@@
 for all unseen points. This is the most basic concept of ML and is used in a variety of applications 
-where labeled data is easy to obtain. Spam mail detection for instance is a case where supervised learning 
-techniques are - among others - used.
+where labeled data is easy to obtain. Spam mail detection for instance is a case where -- among 
+others -- supervised learning techniques are used.
 Many current mail programs have built-in spam detection which originally used
@@
 recognition and OCR are therefore for example used in medical diagnosis to 
-detect cancer on radiographs, in autonomous vehicles to detect obstacles and to 
-stay on track or in post-offices to sort envelopes with hand-written addresses
-\cite{DisciplineOfML:mitchell}.
+detect cancer on radiograms, in autonomous vehicles to detect obstacles and to 
+stay on track or in post-offices to sort envelopes with hand-written 
+addresses\cite{DisciplineOfML:mitchell}.
 
@@
 relatively similar to the way infants learn new things (e.g.\ learning a language) and 
-is used, for example, in clustering data into groups, which we will discuss later\cite{BrainInf:holzinger}.
-Furthermore, nearly all current search machines use unsupervised learning strategies in one fashion or another. 
+is used, for example, in clustering data into groups, which will be discussed later\cite{BrainInf:holzinger}.
+Furthermore, nearly all current search machines use unsupervised learning strategies in one way or another. 
 They mainly use these techniques for \textit{(1) Ranking}, \textit{(2) User classification}\cite{DisciplineOfML:mitchell} 
@@
 it constantly tries to reinforce its learning process and improve its behavior. 
-The learner constantly interacts with its environment to gain new information. A second instance interpretes the 
-actions a learner carries out and rewards it depending on the actions outcome for the environment. The goal of 
+The learner constantly interacts with its environment to gain new information. Another unit interprets the 
+actions carried out by a learner and rewards it depending on the actions outcome for the environment. The goal of 
 the learner now is to maximize its reward over several repetitions. 
@@
 
-\subsection{Self-Optimization}
+\subsection{Self-Optimisation}
 In order to deliver reasonable output, a systems needs to constantly improve itself over its lifetime. Thus, parts of 
@@
 of people with a similar taste in movies.
-Furthermore, clustering can be used to identify communities in social networks, for example for target-advertising, or to cluster location-data so that "important places" of a person can be identified\cite{DJ:frankowski}.
+Furthermore, clustering can be used to identify communities in social networks, for example for target-advertising, or to cluster location-data so that ``important places'' of a person can be identified\cite{DJ:frankowski}.
 
@@
 in order to find centers.
-Classically, data points are tried to be displayed in an n-dimensional metric space and, for example, their Euclidean distance is measured for similarity.
+Classically, data points are tried to be displayed in a n-dimensional metric space and, for example, their Euclidean distance is measured for similarity.
 The Euclidean distance between two data points $p = (p_1, p_2, \dots, p_n)$ and $q = (q_1, q_2, \dots, q_n)$ and thus their
@@
 Another area of application in the field of medical research also takes advantage of human puzzle-solving intuition. 
-For years the project "foldit" of the University of Washington has achieved remarkable results\cite{Foldit:results} from the gamification of a problem related to biology.
+For years the project ``foldit'' of the University of Washington has achieved remarkable results\cite{Foldit:results} from the gamification of a problem related to biology.
 The researchers have developed a game that helps them to optimize and predict possible protein structures with the help of 
@@
 Proteins can fold in a number of different ways. Even with smaller proteins, the number of possible folds can be extremely high due to their many degrees of freedom.
-The aim of the game is to determine the optimal folding and thus the "most comfortable" state of a protein in order to be able to develop appropriate drugs for and with this shape.
+The aim of the game is to determine the optimal folding and thus the ``most comfortable'' state of a protein in order to be able to develop appropriate drugs for and with this shape.
 Since the structure determines the function of a protein\cite{Foldit:web}, new forms can also be used to treat diseases such as AIDS or cancer more effectively.
@@
 The next step towards CIL in this area could be to incorporate the results of human puzzle-solving into the calculations and decisions of ML systems in order to proactively support humans (bi-directional way of inputs, see Section~\ref{sec:intro}) in finding solutions
-for example by excluding unpromisingfls.
+for example by excluding unpromising folds.
 
@@
 The primary goal in manufacturing is to keep production up and running under almost all circumstances. 
-Even short downtimes of production lines result in high sales losses for companies.
+Even short down times of production lines result in high sales losses for companies.
 This is why it is important to keep an eye on the wear of work equipment, production lines and the condition of machines in general at all times.
@@
 
-For CIL-systems, it is conceivable, in addition to the sensor data used by the devices to "measure" wear, to call in expert knowledge, so that rare cases that are easily recognisable as a suspicious situation for humans, can be identified at an early stage by the whole system.
-In this process, a CIL system must estimate at runtime which expert should be asked what and when in order 
+For CIL systems, it is conceivable, in addition to the sensor data used by the devices to ``measure'' wear, to call in expert knowledge, so that rare cases that are easily recognisable as a suspicious situation for humans, can be identified at an early stage by the whole system.
+In this process, a CIL system must estimate at run-time which expert should be asked what and when in order 
 to achieve maximum information content.
@@
 Not only technical difficulties have to be overcome, but also social ones. In order to use ML techniques effectively, 
-at least a minimum amount of data has to be provided in order to be analyzed. To do this, we need to decide 
+at least a minimum amount of data has to be provided in order to be analyzed. To do so, we need to decide 
 to what extent we are willing to disclose our data for the benefits of CIL systems and ML in general.
@@
 (2010, June).
-Finding meaning on youtube: Tag recommendation and category discovery.
+Finding meaning on YouTube: Tag recommendation and category discovery.
 In Computer Vision and Pattern Recognition (CVPR), 2010 IEEE Conference on (pp.
